### 2021-06-17 paper/paper.tex
Commit inicial

\documentclass[a4paper,11pt,twocolumn,twoside]{article}
\usepackage[dvips]{graphicx}
\usepackage{sepln_en}
\usepackage{fullname}
\usepackage[utf8]{inputenc}
\usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}

\input epsf

\setlength\titlebox{4in} %esto por defecto

\title{Título completo del artículo centrado con Times New Roman negrita, tamaño 16}

\author {\textbf{Nombre Apellidos1,$^1$} \textbf{Nombre Apellidos2$^2$}\\
$^1$Universidad o lugar de trabajo\\
$^2$Universidad o lugar de trabajo\\
Información de contacto\\
}

\seplntranstitle{Título traducido del artículo centrado con Times New Roman negrita, cursiva, tamaño 14}

\seplnclave{Palabras, palabras, palabras en castellano...}

\seplnresumen{Resumen del artículo en castellano con una sangría a izquierda y
derecha de 1 cm, justificado por ambos lados, con tamaño de fuente
11.}

\seplnkey{Palabras, palabras, palabras en inglés...}

\seplnabstract{Resumen del artículo en inglés con una sangría a izquierda y
derecha de 1 cm, justificado por ambos lados, con tamaño de fuente
11.}

\firstpageno{1}

\begin{document}

% la siguiente instrucción sólo se debe usar si el abstract sobrescribe el texto
% la longitud variará según se necesite

%\setlength\titlebox{20cm} % se aumenta el tamaño del espacio reservado para datos de título

\label{firstpage} \maketitle

%\begin{abstract}
%Resumen del artículo con una sangría a izquierda y derecha de 0.32
%cm, justificado por ambos lados, con tamaño de fuente 11.
%
%\end{abstract}

\section{Título de nivel uno}

\cite{piad2019general}

\section*{Agradecimientos}

\bibliographystyle{fullname}
\bibliography{bibliography}

\end{document}

### 2021-06-18 paper/paper.tex
Update

@@
 \usepackage[utf8]{inputenc}
-\usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}
+% \usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}
 
@@
 
-\title{Título completo del artículo centrado con Times New Roman negrita, tamaño 16}
+\title{Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021}
 
@@
 
-\seplntranstitle{Título traducido del artículo centrado con Times New Roman negrita, cursiva, tamaño 14}
+\seplntranstitle{Resumen de la Tarea de Descubrimiento de Conocimiento en Salud en IberLEF 2021}
 
@@
 
-\section{Título de nivel uno}
+\section{Introduction}
 
-\cite{piad2019general}
+The vast amount of knowledge stored in natural language
 
-\section*{Agradecimientos}
+How many pieces of knowledge are unconnected, and could lead to new discoveries,
+drug repositioning, trying new medication, finding causes for diseases, just
+by connecting facts and claims in different sources.
+
+Discovering knowledge from text requires assigning a semantic interpretation
+to the text that can be later converted to a data structure (e.g., ontology)
+
+The first step is detect the relevant concepts, or entities mentioned, and how
+they relate to each other
+
+The importance of multi-domain and multi-lingual approaches
+
+Motivation of the challenge
+
+Motivation of the design of a custom annotation schema that is less complex
+than e.g., AMR but still has some formal semantics
+
+Importance of working in low-resource languages and with scarse training data,
+to encourage transfer learning, unsupervised learning, and low cost solutions
+
+\section{Tasks Descriptions}
+
+The eHealth-KD challenge consists on the automatic sentence-level annotation
+of multi-token entities and binary relations among them.
+
+A custom annotation model has been defined, comprising 4 entity types and 13 relations,
+that attempts to capture a large part of factual semantics in technical documents,
+including enciclopedias, news, and scientific papers.
+
+The annotation model is explained in detail in \namecite{piad2019general}.
+
+A brief explanation is presented next.
+
+-- Explicar las entidades y relaciones como siempre.
+
+The challenge has been divided into two different subtasks:
+entity recognition and relation extraction.
+
+To evaluate each subtask, we count correct, partial, missing, and spurious
+annotations, and weight them according to an $F_1$ measure, independently per task.
+
+-- Fórmulas
+
+Furthermore, the challenge is graded in three different scenarios:
+one for each subtask and one where both subtasks are performed in sequence.
+This is the main scenario, which ultimately decides the winner of the challenge,
+although all other results are interesting.
+
+\section{Corpora and Resources}
+
+The Challenge is based on a corpus of documents composed of
+sentences taken from previous challenges and other resources,
+and newly annotated sentences.
+
+Three different sources of textual information are sampled: medline articles,
+wikinews articles, and biomedical papers from the CORD-19 corpus.
+
+The medline and wikinews articles are in Spanish, while CORD are in English.
+
+From the 2019 and 2020 challenges, X sentences where taken.
+
+For this new edition, Y sentences were annotated by a team of annotators.
+The team composition is 4 junior annotators and 3 senior annotators.
+2 junior annotators annotated each sentence, and a senior annotator performed the merging.
+
+The newly annotated sentences are used solely for evaluation purposes,
+while all training and development resources are reused from previous challenges.
+
+Overall, the composition of the corpus is presented in Table~\ref{tab:corpus}.
+
+\begin{table}
+  \caption{Composition of the corpus, highlighting resources from previous
+  challenges and newly annotated sentences.\label{tab:corpus}}
+\end{table}
+
+\section{Systems Descriptions}
+´
+The challenge caught the attention of 8 participants from across the globe,
+who presented a variety of approaches clustered around deep learning architectures.
+
+-- Describir los sistemas
+
+\section{Challenge Results}
+
+Table~\ref{tab:results} summarizes the main results in the challenge.
+
+\begin{table}
+  \caption{Results.\label{tab:results}}
+\end{table}
+
+In Scenario 1, the best performing system is\dots
+
+-- Describir los demás escenarios
+
+\section{Discussion}
+
+-- Ver los sistemas con sus features y qué features son mejores o peores en cada tarea
+
+-- Comparar con los baselines en cada tarea, hasta qué nivel está resuelta cada tarea
+
+-- Hablar brevemente de la evolución de los sistemas en las 4 ediciones,
+cómo se han ido moviendo hacia transformers
+
+-- Hablar de la modelación de las entidades y relaciones como tareas separadas,
+la desventaja que puede representar eso porque los sistemas que han ganado hacen
+ambas cosas a la vez, o sea hay representación conjunta que es válida
+
+-- Hablar de las relaciones como problema binario, que no tiene en cuenta que ciertas
+relaciones implican posiblemente la aparición de otras.
+
+-- Hablar de que el orden en que el humano anota no es el mismo que un sistema,
+y que si se pudiera aprender algo de esto, dar con el dataset no solo las anotaciones
+sino en qué orden fueron realizadas.
+
+-- Hablar de la necesidad de cambiar de tareas hacia algo que refleje el valor
+del conocimiento extraído, como question answering.
+
+\section{Conclusions}
+
+\section*{Acknowledgments}
 

### 2021-06-18 paper/paper.tex
Update Overleaf

@@
 
+The accelerated growth of the Internet and the increased production of textual resources in all areas of human endeavour has created both new opportunities and new challenges for the research community.
+On one hand, larger datasets can be collected and used to build increasingly powerful machine learning models~(e.g., GPT-3 and related).
+On the other hand, is becoming increasingly difficult to organise, categorise, cross-reference, and fact-check the textual information available online.
+The ease of access to both publication and consumption of textual information is also one of the causes of the increasingly worrying phenomena of fake news.
+
 The vast amount of knowledge stored in natural language
@@
 
-Importance of working in low-resource languages and with scarse training data,
+Importance of working in low-resource languages and with scarce training data,
 to encourage transfer learning, unsupervised learning, and low cost solutions

### 2021-06-18 paper/paper.tex
Intro lista

@@
 On the other hand, is becoming increasingly difficult to organise, categorise, cross-reference, and fact-check the textual information available online.
-The ease of access to both publication and consumption of textual information is also one of the causes of the increasingly worrying phenomena of fake news.
+The ease of access to both publication and consumption of textual information is arguably one of the root causes of the increasingly worrying phenomenon of fake news.
 
-The vast amount of knowledge stored in natural language
+Staying up-to-date on information about topics of interest is crucial in technical or scientific domains.
+For this purpose, specialists rely on a combination of curated soruces (e.g., domain-specific repositories like arxiv, bioarxiv, semantic scholar) and technologies for search and recommendation (e.g., google scholar).
+These resources significantly improve the experience of collecting and consuming large amounts of relevant information on a specific topic.
+Tools like Connected Papers~\cite{} and Papers with Code~\cite{} are one step beyond the indexing of documents, providing summarised and structured representations of the content in a collection of documents.
+However, it remains an open problem to automatically combine, summarise, and present the relevant information in a collection of documents in a semantic structure~(e.g., a knowledge graph) that allows a specialist to quickly grasp the essential concepts of a specific knowledge field.
 
-How many pieces of knowledge are unconnected, and could lead to new discoveries,
-drug repositioning, trying new medication, finding causes for diseases, just
-by connecting facts and claims in different sources.
+A potential solution to this problem would require methods to automatically detect in natural language the most relevant concepts and the factual statements in which they are related, possibly normalise them into well-established taxonomies and classifications, and store them in computational data structures where they can linked with related concepts, e.g., knowledge graphs.
+The first step of this process, i.e., the detection of relevant concepts and semantic relations in text, is already a challenging computational task, given the complexity and variability of natural language.
+To encourage research and development in this area, several academic competitions have been organised through the years by organizations such as CLEF, SEMEVAL, and more recently, IBERLEF.
 
-Discovering knowledge from text requires assigning a semantic interpretation
-to the text that can be later converted to a data structure (e.g., ontology)
+In this context, the eHealth Knowledge Discovery Challenge is designed to foster the development of automatic knowledge discovery systems for natural language sentences in a cross-domain and multi-lingual setting.
+Concretely, a token-level annotation model of 4 entities and 13 semantic relations is defined, and a corpus of more than 1500 sentences from different factual sources~(i.e., Spanish Medline articles, Spanish Wikinews articles, and English biomedical preprints related to COVID-19) is annotated.
+Two computational tasks are defined: the detection of multi-span, non-contiguous, and potentially overlapping named entities; and the detection of semantic relations between them.
+A shared annotation campaign was organized, where a total of 9 participants presented 10 different systems with varied levels of performance.
 
-The first step is detect the relevant concepts, or entities mentioned, and how
-they relate to each other
+The eHealth-KD task focuses on cross-domain, multi-lingual and low-resource solutions.
+This setting presents a significant challenge to existing state-of-the-art methods, which often rely on large amounts of training data.
+A succesful approach to the eHealth-KD must leverage transfer learning across both different domains and languages, since the vast majority of the training examples are provided in Spanish language and Medline articles, while only a small development set is available in the remaining settings.
+With this added complexity, we expect to encourage solutions that can be deployed in low-resource environments, where is unfeasible to train large language models over longs periods of time.
 
-The importance of multi-domain and multi-lingual approaches
+The remaining of this paper is organized as follows.
+Section~\ref{sec:task} describes the eHealth-KD tasks in greater detail, including the annotation model and performance metrics.
+Section~\ref{sec:resources} describes the corpora and other resources created for this challenge and presents some qualitative analysis of their characteristics.
+Section~\ref{sec:systems} describes the different systems presented in the challenge and summarises the main approaches and most common characteristics they share.
+Section~\ref{sec:results} presents the main results of the challenge.
+Section~\ref{sec:discussion} discusses the most interesting insights of the challenge and highlights both the most relevant lessons learned and potential improvements for future similar endeavours.
 
-Motivation of the challenge
-
-Motivation of the design of a custom annotation schema that is less complex
-than e.g., AMR but still has some formal semantics
-
-Importance of working in low-resource languages and with scarce training data,
-to encourage transfer learning, unsupervised learning, and low cost solutions
-
-\section{Tasks Descriptions}
+\section{Tasks Descriptions}\label{sec:task}
 
@@
 
-\section{Corpora and Resources}
+\section{Corpora and Resources}\label{sec:resources}
 
@@
 
-\section{Systems Descriptions}
+\section{Systems Descriptions}\label{sec:systems}
 ´
@@
 
-\section{Challenge Results}
+\section{Challenge Results}\label{sec:results}
 
@@
 
-\section{Discussion}
+\section{Discussion}\label{sec:discussion}
 
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{sec:conclusions}
 

### 2021-06-18 paper/paper.tex
Sistemas

--- 2021-06-18 paper/paper.tex
@@
 
--- Describir los sistemas
+%-- Describir los sistemas
+\begin{description}
+  \item[uhKD4:]  system is built upon two independent deep-learning-based architectures. Accordingly, two
+  different models are defined and each task is carried out separately. Task A is approached as a
+  sequence labelling problem in which each token from an input sequence is assigned a label that
+  represents the combination of the BILUOV entity tagging scheme with each one of the possible
+  types of an entity. The BILUOV tags correspond to: Begin, to represent the start of an entity;
+  Inner, to represent its continuation; Last, to represent its end; Unit, to represent single word
+  entities; Other, to represent words that are not a part of any entity; and oVerlapping, to represent
+  words that belong to multiple entities.Thus, the output of the model considers 21 different labels: the
+  O label and the combination of the remaining tags (BILUV) and the entity types (Concept,
+  Action, Predicate and Reference). The proposed approach to Task B is to solve a multi-class
+  classification problem, in which given a sentence and a highlighted pair of entities, one of the
+  predefined relations is assigned to occur from the first entity toward the second one. A new
+  artificial relation class none is defined to symbolize the non-occurrence of any relation between
+  a pair of entities.
+
+  \item[Vicomtech Joint Classifier:] This model is the result of the revision of our participation in the previous eHealth-KD edition
+  [2]. Most of the changes introduced in the current edition aim at simplifying components of
+  the architecture that seemed redundant or needlessly complex. In addition, we have forgone
+  the ability to predict multi-word discontinuous and/or overlapping entities like the shown in
+  Figure 1, which in any case required elaborate post-processing to yield acceptable results.
+  It consists of a single end-to-end deep neural network with
+  pre-trained BERT models as the core for the semantic representation of the input texts, that predicts all
+  the output variables—entities and relations—at the same time, modelling the whole problem jointly.
+  The main change w.r.t. the original implementation affects the representation of relations. The Joint
+  Classifier model achieved the first position in the main scenario of the competition and ranked second
+  in the rest of the scenarios.
+
+  \item[Vicomtech  Seq2Seq:] uses an approach based on an
+  encoder-decoder model. It transduces the input text into an output sequence by reading the input text.
+  The target sequence is a compact representation of the information contained in the gold-labels of
+  the datasets. This approach showed a promising performance despite not being competitive enough.
+  However, it poses an interesting potential future work.
+  This paradigm is way more flexible because it can ingest a sequence of any length,
+  and output another arbitrary sequence. That is, the output sequence is not tied to the structure
+  of the input; a text-to-text model can potentially encode any sort of information
+
+  \item[PUCRJ-PUCPR-UFMG:] a multilingual BERT-based system for joint entity recognition and relation extraction
+  in multidomain texts. Our end-to-end multitasking model benefits from the transformer architecture,
+  which has proved to capture better the global dependencies of the input text. Also, the use of a multilin-
+  gual model contributed to our system to perform well even in the set of tests containing non-Spanish
+  sentences. The method consists in an end-to-end multilingual
+  BERT-based system that jointly predicts both entities and relations. During training, the
+  proposed multi-task system is fine-tuned in 3 sequential steps: the first one prioritizes the entity
+  recognition task whereas the second gives precedence to the relation extraction one. Finally,
+  the third and last step is trained for both tasks using a multi-task strategy.
+
+  \item[UH-MMM:]  solution solves both tasks separately and sequentially. Thus, independent models
+  with different architectures and features were trained to solve the NER and RE problems. The
+  main distinction between the two architectures raises from the type of problem they solve. The
+  first task is posed as a tag prediction problem that takes the raw text of a sentence as input and
+  outputs two independent tag sequences: one in the BILOUV tag system for entity prediction and
+  another with the tags corresponding to each entity type (Concept, Action, Reference, Predicate).
+  The BILOUV tag scheme classification corresponds to Begin, for the start of an entity; Inner, for
+  the token in the middle; Last for the ending token; Unit, to represent single token entities; Other
+  to represent tokens that do not belong to any entity, and the oVerlapping tag is used to deal
+  with tokens that belong to multiple entities. On the other hand, the second task is addressed as
+  a series of pairwise queries among the entities present in the target sentence, oriented towards
+  identifying the relevant relations between the previously extracted entities.
+
+  \item[(IXA):]  use the pre-trained Language Model (LM), namely XML-
+  RoBERTa-base, to provide a Cross-lingual representation of tokens and the ability to transfer learning
+  from general domains. system was
+  designed as a pipeline of generic sequence labellers, each of them independently fine-tuned for each
+  subtask. The generic sequence labeller consists of a feed-forward network that learns how to align
+  a sequence of tokens into a sequence of labels regardless of the language and domain. This simple
+  straightforward system ranked in the third position in the main and Entity recognition scenario and
+  widely outperformed the other systems in the relation extraction scenario.
+
+  \item[Maoqin:]  Several deep learning models are used in plain text documents, such as
+  BERT-CRF, BiLSTM-CRF. Only the best result running in the local has been submitted. But the final
+  result of my method is indeed very low, with a score of 0.173 (F1), ranking 9th on the leaderboard.
+  Additional work needs to be done to improve our final result and complete the subtask B: relation
+  extraction.
+
+  \item[Maoquin:] For one method, the pre-trained BERT model has been taken as the basic representation.
+  For another method, BiLSTM has been preferred. The system achieved unsatisfied results in the
+  challenge for official evaluation in subtask A. Due to the colab’s time and resources limitation,
+  some strategies were not achieved. And subtask B: Relation Extraction has not been completed.
+
+  \item [GuanZhengyi:] . We mainly used the classic BERT+BiLSTMs+CRF model architecture and replaced BERT
+  with BETO as the pre-training model. BETO is a BERT model pre-training on Spanish text. And we
+  add CNN before BiLSTM for further feature extraction. Our model architecture performed well in the
+  training set and development set for identifying the types of entities
+  uses the pre-training model BETO with stronger text feature
+  representation capabilities as the feature representation layer. After reading the eHealth 2020
+  papers, we fine-tuned the above architecture. We added CNN to further extract features of
+  text. We regard NER as a classification problem at the token level. We combined BETO with
+  CNN, BiLSTM and CRF model to extract global and local features of the text. That means we
+  input these word vectors into CNN, BiLSTM and CRF to calculate the corresponding scores and
+  perform entity recognition and BIO labeling.
+\end{description}
 

### 2021-06-19 paper/paper.tex
agregando sistemas

--- 2021-06-18 paper/paper.tex
@@
   perform entity recognition and BIO labeling.
+
+  \item[JAD:] The model consist of identifying key-phrases
+  and relations among them using a pre-defined system. It was a simple model that summarizes
+  some parts of a general approach to NLP problem. The system is easy to train and test using
+  cloud services like Google Colab. It did not perform very well at the competition.
+  Our system is based on a pre-trained multi-lingual BERT[2] layer which pre-processes the input sentence and then feeds the generated
+embeddings to the deep learning model. 
 \end{description}

### 2021-06-19 paper/paper.tex
Update

--- 2021-06-18 paper/paper.tex
@@
 This setting presents a significant challenge to existing state-of-the-art methods, which often rely on large amounts of training data.
-A succesful approach to the eHealth-KD must leverage transfer learning across both different domains and languages, since the vast majority of the training examples are provided in Spanish language and Medline articles, while only a small development set is available in the remaining settings.
+A succesful approach to the eHealth-KD must leverage transfer learning across different domains and languages, since the vast majority of the training examples are provided in Spanish language and from the Medline domain, while only a small development set is available in the remaining settings.
 With this added complexity, we expect to encourage solutions that can be deployed in low-resource environments, where is unfeasible to train large language models over longs periods of time.
@@
   Additional work needs to be done to improve our final result and complete the subtask B: relation
-  extraction.
-
-  \item[Maoquin:] For one method, the pre-trained BERT model has been taken as the basic representation.
+  extraction. For one method, the pre-trained BERT model has been taken as the basic representation.
   For another method, BiLSTM has been preferred. The system achieved unsatisfied results in the

### 2021-06-19 paper/paper.tex
Update

--- 2021-06-19 paper/paper.tex
@@
 \usepackage[utf8]{inputenc}
+\usepackage{booktabs}
+\usepackage{tabularx}
 % \usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}
@@
 \section{Systems Descriptions}\label{sec:systems}
-´
+
 The challenge caught the attention of 8 participants from across the globe,
 who presented a variety of approaches clustered around deep learning architectures.
+Table~\ref{tab:participants} summarises the main characteristics of each approach presented.
+A brief summary of each system follows:
+
+\begin{table*}[ht]
+  \centering
+  \begin{tabularx}{\textwidth}{lXllll}
+    \toprule
+    System & Features & Tasks & Subtask A & Subtask B & Multi-span \\
+    \midrule
+    Codestrange & 				 \\
+    GuanZhengyi & BETO & Only A & Sequence & - & BIO \\
+    IXA & ROBERTa & Sequential & Sequence & Sequence & BIO \\
+    JAD & BERT & Joint & Token & Pairwise & Relation \\
+    Maoqin & BERT & Only A & Sequence & - & BIO \\
+    PUCRJ-PUCPR-UFMG & BERT & Joint & Sequence & Pairwise & BIO \\
+    uhKD4 & Word2vec POS-tag Character Position & Sequential & Sequence & Pairwise & BILOUV \\
+    UH-MMM & BERT FastText POS-tag Dependency Character & Sequential & Sequence & Pairwise & BILOUV \\
+    Vicomtech Joint & BERT & Joint & Sequence & Pairwise & BIO \\
+    Vicomtech Seq2Seq & T5 & Joint & Text2text & Text2text & Text \\
+    \bottomrule
+  \end{tabularx}
+  \caption{Summary of the approaches presented at the eHealth-KD Challenge.\label{tab:participants}}
+\end{table*}
 
@@
 \begin{description}
-  \item[uhKD4:]  system is built upon two independent deep-learning-based architectures. Accordingly, two
-  different models are defined and each task is carried out separately. Task A is approached as a
-  sequence labelling problem in which each token from an input sequence is assigned a label that
-  represents the combination of the BILUOV entity tagging scheme with each one of the possible
-  types of an entity. The BILUOV tags correspond to: Begin, to represent the start of an entity;
-  Inner, to represent its continuation; Last, to represent its end; Unit, to represent single word
-  entities; Other, to represent words that are not a part of any entity; and oVerlapping, to represent
-  words that belong to multiple entities.Thus, the output of the model considers 21 different labels: the
-  O label and the combination of the remaining tags (BILUV) and the entity types (Concept,
-  Action, Predicate and Reference). The proposed approach to Task B is to solve a multi-class
-  classification problem, in which given a sentence and a highlighted pair of entities, one of the
-  predefined relations is assigned to occur from the first entity toward the second one. A new
-  artificial relation class none is defined to symbolize the non-occurrence of any relation between
-  a pair of entities.
+  \item[Team Codestrange] proposes
 
-  \item[Vicomtech Joint Classifier:] This model is the result of the revision of our participation in the previous eHealth-KD edition
-  [2]. Most of the changes introduced in the current edition aim at simplifying components of
-  the architecture that seemed redundant or needlessly complex. In addition, we have forgone
-  the ability to predict multi-word discontinuous and/or overlapping entities like the shown in
-  Figure 1, which in any case required elaborate post-processing to yield acceptable results.
-  It consists of a single end-to-end deep neural network with
-  pre-trained BERT models as the core for the semantic representation of the input texts, that predicts all
-  the output variables—entities and relations—at the same time, modelling the whole problem jointly.
-  The main change w.r.t. the original implementation affects the representation of relations. The Joint
-  Classifier model achieved the first position in the main scenario of the competition and ranked second
-  in the rest of the scenarios.
+  \item[Team GuanZhengy~\cite{guanzhengyi}] presents a traditional NER architecture for Subtask A, based on contextual embeddings from a BETO pre-trained language model, and a combination of Convolutional, Bi-LSTM, and CRF layers for decoding BIO tags.
 
-  \item[Vicomtech  Seq2Seq:] uses an approach based on an
-  encoder-decoder model. It transduces the input text into an output sequence by reading the input text.
-  The target sequence is a compact representation of the information contained in the gold-labels of
-  the datasets. This approach showed a promising performance despite not being competitive enough.
-  However, it poses an interesting potential future work.
-  This paradigm is way more flexible because it can ingest a sequence of any length,
-  and output another arbitrary sequence. That is, the output sequence is not tied to the structure
-  of the input; a text-to-text model can potentially encode any sort of information
+  \item[Team IXA~\cite{ixa}] models both substasks are sequence labeling problems encoded with a BIO system and using a pre-trained XLM-RoBERTa language model.
+Subtask A is solved with a standard NER architecture.
+For Subtask B, they solve a sequence labelling problem for each pair of entities, where tags correspond to relation labels.
 
-  \item[PUCRJ-PUCPR-UFMG:] a multilingual BERT-based system for joint entity recognition and relation extraction
-  in multidomain texts. Our end-to-end multitasking model benefits from the transformer architecture,
-  which has proved to capture better the global dependencies of the input text. Also, the use of a multilin-
-  gual model contributed to our system to perform well even in the set of tests containing non-Spanish
-  sentences. The method consists in an end-to-end multilingual
-  BERT-based system that jointly predicts both entities and relations. During training, the
-  proposed multi-task system is fine-tuned in 3 sequential steps: the first one prioritizes the entity
-  recognition task whereas the second gives precedence to the relation extraction one. Finally,
-  the third and last step is trained for both tasks using a multi-task strategy.
+  \item[Team JAD~\cite{jad}] proposes a single model based on BERT pre-trained embeddings that jointly outputs entity labels~(at token level) and pairwise relation labels.
+To deal with multi-span entities, they add a virtual relation that links tokens from the same entity.
 
-  \item[UH-MMM:]  solution solves both tasks separately and sequentially. Thus, independent models
-  with different architectures and features were trained to solve the NER and RE problems. The
-  main distinction between the two architectures raises from the type of problem they solve. The
-  first task is posed as a tag prediction problem that takes the raw text of a sentence as input and
-  outputs two independent tag sequences: one in the BILOUV tag system for entity prediction and
-  another with the tags corresponding to each entity type (Concept, Action, Reference, Predicate).
-  The BILOUV tag scheme classification corresponds to Begin, for the start of an entity; Inner, for
-  the token in the middle; Last for the ending token; Unit, to represent single token entities; Other
-  to represent tokens that do not belong to any entity, and the oVerlapping tag is used to deal
-  with tokens that belong to multiple entities. On the other hand, the second task is addressed as
-  a series of pairwise queries among the entities present in the target sentence, oriented towards
-  identifying the relevant relations between the previously extracted entities.
+  \item[Team Maoquin~\cite{maoquin}] presents a traditional NER architecture based on BERT pre-trained embeddings and BIO tags for Subtask A, combined with Bi-LSTM and CRF layers.
 
-  \item[(IXA):]  use the pre-trained Language Model (LM), namely XML-
-  RoBERTa-base, to provide a Cross-lingual representation of tokens and the ability to transfer learning
-  from general domains. system was
-  designed as a pipeline of generic sequence labellers, each of them independently fine-tuned for each
-  subtask. The generic sequence labeller consists of a feed-forward network that learns how to align
-  a sequence of tokens into a sequence of labels regardless of the language and domain. This simple
-  straightforward system ranked in the third position in the main and Entity recognition scenario and
-  widely outperformed the other systems in the relation extraction scenario.
+  \item[Team PUCRJ-PUCPR-UFMG~\cite{pucrj}] proposes a joint model that outputs token labels~(modelled as a sequence labelling problem) and pairwise relation labels, based on BERT pre-trained embeddings as the main feature.
 
-  \item[Maoqin:]  Several deep learning models are used in plain text documents, such as
-  BERT-CRF, BiLSTM-CRF. Only the best result running in the local has been submitted. But the final
-  result of my method is indeed very low, with a score of 0.173 (F1), ranking 9th on the leaderboard.
-  Additional work needs to be done to improve our final result and complete the subtask B: relation
-  extraction. For one method, the pre-trained BERT model has been taken as the basic representation.
-  For another method, BiLSTM has been preferred. The system achieved unsatisfied results in the
-  challenge for official evaluation in subtask A. Due to the colab’s time and resources limitation,
-  some strategies were not achieved. And subtask B: Relation Extraction has not been completed.
+  \item[Team uhKD4~\cite{uhkd4}] models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
+As features, they employ a variety of syntactic characteristics~(POS-tags, character embeddings, positional embeddings) as well as word2vec embeddings.
 
-  \item [GuanZhengyi:] . We mainly used the classic BERT+BiLSTMs+CRF model architecture and replaced BERT
-  with BETO as the pre-training model. BETO is a BERT model pre-training on Spanish text. And we
-  add CNN before BiLSTM for further feature extraction. Our model architecture performed well in the
-  training set and development set for identifying the types of entities
-  uses the pre-training model BETO with stronger text feature
-  representation capabilities as the feature representation layer. After reading the eHealth 2020
-  papers, we fine-tuned the above architecture. We added CNN to further extract features of
-  text. We regard NER as a classification problem at the token level. We combined BETO with
-  CNN, BiLSTM and CRF model to extract global and local features of the text. That means we
-  input these word vectors into CNN, BiLSTM and CRF to calculate the corresponding scores and
-  perform entity recognition and BIO labeling.
+  \item[Team UH-MMM~\cite{uhmmm}] also models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
+As a key characteristic, they encode the shortest dependency path between two entities for the relation predction.
+They also compare several different embeddings, including health-specific and general-purpose approaches.
+
+  \item[Team Vicomtech~\cite{vicomtech}] presents two different models.
+The first consists of a joint architecture for sequence labelling~(Subtask A) and pairwise relation prediciton~(Subtask B) based on BERT pre-trained embeddings.
+The second model is a text-to-text architecture, based on a T5 model, finetunned on a problem-specific encoding of the entities and relations that solves both subtasks in a single pass.
 \end{description}
+
+-- Describir ideas generales más usadas
 

### 2021-06-19 paper/paper.tex
Update

@@
 
+-- hablar de los 2 enfoques raros IXA y Vicomtech, que puede aportar cada uno.
+IXA que lo hacen por cada par de entidades, y se podría hacer para toda la oración a la vez, o al menos para todos los orígenes.
+Vicomtech que tienen problemas con que T5 alucina frases que no están en el texto, que si se podría restringir a output solamente lo que está en la oración original.
+Además que tienen que generar las mismas entidades varias veces, porque hay más relaciones que entidades, una representación más compacta que solo tenga las relaciones puede ayudar.
+
 -- Hablar de que el orden en que el humano anota no es el mismo que un sistema,

### 2021-06-19 paper/paper.tex
texto de los sistemas

--- 2021-06-19 paper/paper.tex
@@
 
+How can see in the table \ref{} BERT and variants predominate as feature extractor although
+some teams add clasic NLP featuures.
+In contrast with previus years the join aproche is used by more than the half of system that present in the involve task
+Como en años anteriores the subtask A is model as sequens labeling using some variant of BIO encoding. 
+Likewise the subtask B is commonly model as pair wise classification.
+
+Two approaches break this treads IXA and VICONTECH, The fisrt model the task B
+also as sequence labeling reusing the same arquitecture that subtask A.
+Th second present a arquitecture text to text that translate que raw sentence To
+a semiestructured representation where are encode all the entities and their relations.
+
 \section{Challenge Results}\label{sec:results}

### 2021-06-19 paper/paper.tex
texto del sitio tarea y corpus

@@
 
+\subsection{Subtask A: Entity recognition}
+Given a list of eHealth documents written in Spanish, the goal of this subtask is to identify all the entities per document and their types.
+These entities are all the relevant terms (single word or multiple words) that represent semantically important elements in a sentence.
+The following figure shows the relevant entities that appear in a set of example sentences.
+
+Entities will always consist of one or more complete words (i.e., not a prefix or a suffix of a word), and will never include any surrounding punctuation symbols, parenthesis, etc.
+There are four types for entities:
+
+Concept: indentifies a relevant term, concept, idea, in the knowledge domain of the sentence.
+Action: indentifies a process or modification of other entities.
+It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition), where it denotes the act of being exposed to the Sun, and “daños” (damages), where it denotes the act of damaging the skin.
+It can also be used to indicate non-verbal functional relations, such as “padre” (parent), etc.
+Predicate: identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) with some additional arguments such as “60 años” (60 years).
+Reference: identifies a textual element that refers to an entity –of the same sentence or of different one–, which can be indicated by textual clues such as “esta”, “aquel”, etc.
+
+\subsection{Subtask B: Relation extraction}
+
+Subtask B continues from the output of Subtask A, by linking the entities detected and labelled in the input document.
+The purpose of this subtask is to recognize all relevant semantic relationships between the entities recognized.
+
+The semantic relations are divided in different categories:
+
+General relations (6): general-purpose relations between two concepts (it involves Concept, Action, Predicate, and Reference) that have a specific semantic.
+When any of these relations applies, it is preferred over a domain relation –tagging a key phrase as a link between two information units–, since their semantic is independent of any textual label:
+
+is-a: indicates that one entity is a subtype, instance, or member of the class identified by the other.
+same-as: indicates that two entities are semantically the same.
+has-property: indicates that one entity has a given property or characteristic.
+part-of: indicates that an entity is a constituent part of another.
+causes: indicates that one entity provoques the existence or occurrence of another.
+entails: indicates that the existence of one entity implies the existence or occurrence of another.
+Contextual relations (3): allow to refine an entity (it involves Concept, Action, Predicate, and Reference) by attaching modifiers. These are:
+
+in-time: to indicate that something exists, occurs or is confined to a time-frame, such as in “exposición” in-time “verano”.
+in-place: to indicate that something exists, occurs or is confined to a place or location.
+in-context: to indicate a general context in which something happens, like a mode, manner, or state, such as “exposición” in-context “prolongada”.
+Action roles (2): indicate which role play the entities related to an Action:
+
+subject: indicates who performs the action, such as in “[el] asma afecta […]”.
+target: indicates who receives the effect of the action, such as in “[…] afecta [las] vías respiratorias”.
+Actions can have several subjects and targets, in which case the semantic interpreted is that the union of the subjects performs the action over each of the targets.
+Predicate roles (2): indicate which role play the entities related to a Predicate:
+
+domain: indicates the main entity on which the predicate applies.
+arg: indicates an additional entity that specifies a value for the predicate to make sense.
+The exact semantic of this argument depends on the semantic of the predicate label, such as in “mayores [de] 60 años”, where the predicate label “mayores” indicates that “60 años” is a quantity, that restricts the minimum age for the predicate to be true.
+
+\subsection{Evaluation}
+
 To evaluate each subtask, we count correct, partial, missing, and spurious
@@
 -- Fórmulas
+Rec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + M_A + M_B}
+
+Prec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + S_A + S_B}
+
+F_{1AB} = 2 \cdot \frac{Prec_{AB} \cdot Rec_{AB}}{Prec_{AB} + Rec_{AB}}
 
@@
 
-Three different sources of textual information are sampled: medline articles,
-wikinews articles, and biomedical papers from the CORD-19 corpus.
+For the eHealth-KD 2021 edition, systems will be evaluated in a cross-domain and multi-language corpus. 
+Both the training, development, and test collections will contain sentences extracted from MedlinePlus, Wikinews, and the CORD-19 corpus, 
+all of them related with health topics, but showing a significant variety in terms of format and structure. 
+Furthermore, the majority of sentences are in Spanish, but a small set of English sentences is also included, to evaluate generalization across domains.
 
-The medline and wikinews articles are in Spanish, while CORD are in English.
+In the training collection, each sentence will be labeled with its corresponding domain and language (Spanish or English), 
+so that participants can potentially fine-tune different models for each domain/language and learn to identify them in the text. 
+In the development collection, sentences will be mixed from all different sources and no labelling will be provided, 
+so that participants can evaluate their systems in a similar environment to the testing set.
+
+Participants can opt-out of the cross-domain / multi-language challenge at evaluation time, 
+in which case only the metrics from the main domain (MedlinePlus) and language (Spanish) will be used.
+
+As in the previous edition, the corpus for eHealth-KD 2021 will use a corpus extracted from MedlinePlus sources, plus additional resources. 
+First, the same corpus used in the 2020 edition will be provided for training and development, while a new set of previously unlabelled sentences will be manually annotated and used for the test collection.
+Additionally, health-related news sourced from Wikinews will be also provided for training and development.
+Finally, a small set of sentences from scientific papers in the CORD-19 corpus (in English language) will be selected, annotated, and distributed in the development, and testing collections.
+
+%Three different sources of textual information are sampled: medline articles,
+%wikinews articles, and biomedical papers from the CORD-19 corpus.
+
+The corpus will be divided into three sections. Training and development sets are published along with baseline implementations, 
+for participants to train and fine-tune their systems. These files consist of both plain text input and the expected outputs for both subtasks.
+
+%The medline and wikinews articles are in Spanish, while CORD are in English.
 
@@
 while all training and development resources are reused from previous challenges.
+
+contains 3000 sentences. The first 2700 are in Spanish and the last 300 are in English. Of these, only 50 in each language will 
+be used for evaluation (the rest are provided to discourage manual annotation), but you must output annotations for all of the sentences,
+since the reference sentences are shuffled.
 

### 2021-06-19 paper/paper.tex
Add results

--- 2021-06-19 paper/paper.tex
@@
 
-\section{Systems Descriptions}\label{sec:systems}
-
-The challenge caught the attention of 8 participants from across the globe,
-who presented a variety of approaches clustered around deep learning architectures.
-Table~\ref{tab:participants} summarises the main characteristics of each approach presented.
-A brief summary of each system follows:
-
-\begin{table*}[ht]
+\begin{table*}[t!]
   \centering
@@
 \end{table*}
+
+\section{Systems Descriptions}\label{sec:systems}
+
+The challenge caught the attention of 8 participants from across the globe,
+who presented a variety of approaches clustered around deep learning architectures.
+Table~\ref{tab:participants} summarises the main characteristics of each approach presented.
+A brief summary of each system follows:
 
@@
 
-\begin{table}
+\begin{table*}
+  \resizebox{\textwidth}{!}{
+  \begin{tabular}{lccccccccc}
+    \toprule
+    & \multicolumn{3}{c}{\textbf{Main}} & \multicolumn{3}{c}{\textbf{Task A}} & \multicolumn{3}{c}{\textbf{Task B}} \\
+    \textbf{Team}    & $F_1$ & $P$   & $R$   & $F_1$ & $P$   & $R$   & $F_1$ & $P$   & $R$ \\
+    \midrule
+    Vicomtech        & 0.531 & 0.540 & 0.534 & 0.684 & 0.699 & 0.747 & 0.371 & 0.541 & 0.283 \\
+    PUCRJ-PUCPR-UFMG & 0.528 & 0.568 & 0.502 & 0.706 & 0.714 & 0.697 & 0.263 & 0.366 & 0.205 \\
+    IXA              & 0.498 & 0.464 & 0.538 & 0.653 & 0.613 & 0.698 & 0.430 & 0.453 & 0.409 \\
+    uhKD4            & 0.422 & 0.485 & 0.374 & 0.527 & 0.517 & 0.537 & 0.317 & 0.556 & 0.222 \\
+    UH-MMM           & 0.338 & 0.291 & 0.403 & 0.607 & 0.546 & 0.685 & 0.053 & 0.077 & 0.041 \\
+    Codestrange      & 0.232 & 0.337 & 0.176 & 0.080 & 0.415 & 0.044 & 0.032 & 0.437 & 0.017 \\
+    baseline         & 0.232 & 0.337 & 0.176 & 0.306 & 0.350 & 0.271 & 0.032 & 0.437 & 0.017 \\
+    JAD              & 0.109 & 0.234 & 0.071 & 0.262 & 0.315 & 0.224 & 0.007 & 0.375 & 0.003 \\
+    GuanZhengyi      & -     & -     & -     & 0.334 & 0.520 & 0.245 & -     & -     & -     \\
+    Maoqin           & -     & -     & -     & 0.173 & 0.271 & 0.127 & -     & -     & -     \\
+    \bottomrule
+  \end{tabular}}
+
   \caption{Results.\label{tab:results}}
-\end{table}
+\end{table*}
 

### 2021-06-19 paper/paper.tex
arreglando fórmulas
Update

@@
 
-To evaluate each subtask, we count correct, partial, missing, and spurious
+To evaluate each subtask, we count correct, incorrect, partial, missing, and spurious
 annotations, and weight them according to an $F_1$ measure, independently per task.
+Partial annotations~(i.e., where predicted entities overlap with the gold standard) are counted as half the value of correct annotations.
 

### 2021-06-19 paper/paper.tex
Add figure

@@
 \documentclass[a4paper,11pt,twocolumn,twoside]{article}
-\usepackage[dvips]{graphicx}
+\usepackage{graphicx}
 \usepackage{sepln_en}
@@
 including enciclopedias, news, and scientific papers.
+The annotation model is explained in detail in \namecite{piad2019general}.
+Figure~\ref{fig:model} shows an illustrative example of the annotation model in three Spanish sentences.
+The challenge has been divided into two different subtasks: entity recognition and relation extraction.
 
-The annotation model is explained in detail in \namecite{piad2019general}.
-
-A brief explanation is presented next.
-
--- Explicar las entidades y relaciones como siempre.
-
-The challenge has been divided into two different subtasks:
-entity recognition and relation extraction.
+\begin{figure*}
+  \includegraphics[width=\textwidth]{model.png}
+  \caption{Examples the annotation model defined for the eHealth-KD Challenge.\label{fig:model}}
+\end{figure*}
 
 \subsection{Subtask A: Entity recognition}
+
 Given a list of eHealth documents written in Spanish, the goal of this subtask is to identify all the entities per document and their types.
@@
 
-Concept: indentifies a relevant term, concept, idea, in the knowledge domain of the sentence.
-Action: indentifies a process or modification of other entities.
+\begin{description}
+  \item[Concept:] indentifies a relevant term, concept, idea, in the knowledge domain of the sentence.
+  \item[Action:] indentifies a process or modification of other entities.
 It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition), where it denotes the act of being exposed to the Sun, and “daños” (damages), where it denotes the act of damaging the skin.
 It can also be used to indicate non-verbal functional relations, such as “padre” (parent), etc.
-Predicate: identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) with some additional arguments such as “60 años” (60 years).
-Reference: identifies a textual element that refers to an entity –of the same sentence or of different one–, which can be indicated by textual clues such as “esta”, “aquel”, etc.
+  \item[Predicate:] identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) with some additional arguments such as “60 años” (60 years).
+  \item[Reference:] identifies a textual element that refers to an entity –of the same sentence or of different one–, which can be indicated by textual clues such as “esta”, “aquel”, etc.
+\end{description}
 
@@
 
-General relations (6): general-purpose relations between two concepts (it involves Concept, Action, Predicate, and Reference) that have a specific semantic.
+\paragraph{General relations (6)}: general-purpose relations between two concepts (it involves Concept, Action, Predicate, and Reference) that have a specific semantic.
 When any of these relations applies, it is preferred over a domain relation –tagging a key phrase as a link between two information units–, since their semantic is independent of any textual label:
 
-is-a: indicates that one entity is a subtype, instance, or member of the class identified by the other.
-same-as: indicates that two entities are semantically the same.
-has-property: indicates that one entity has a given property or characteristic.
-part-of: indicates that an entity is a constituent part of another.
-causes: indicates that one entity provoques the existence or occurrence of another.
-entails: indicates that the existence of one entity implies the existence or occurrence of another.
-Contextual relations (3): allow to refine an entity (it involves Concept, Action, Predicate, and Reference) by attaching modifiers. These are:
+\begin{description}
+  \item[is-a:] indicates that one entity is a subtype, instance, or member of the class identified by the other.
+  \item[same-as:] indicates that two entities are semantically the same.
+  \item[has-property:] indicates that one entity has a given property or characteristic.
+  \item[part-of:] indicates that an entity is a constituent part of another.
+  \item[causes:] indicates that one entity provoques the existence or occurrence of another.
+  \item[entails:] indicates that the existence of one entity implies the existence or occurrence of another.
+\end{description}
 
-in-time: to indicate that something exists, occurs or is confined to a time-frame, such as in “exposición” in-time “verano”.
-in-place: to indicate that something exists, occurs or is confined to a place or location.
-in-context: to indicate a general context in which something happens, like a mode, manner, or state, such as “exposición” in-context “prolongada”.
-Action roles (2): indicate which role play the entities related to an Action:
+\paragraph{Contextual relations (3)}: allow to refine an entity (it involves Concept, Action, Predicate, and Reference) by attaching modifiers. These are:
 
-subject: indicates who performs the action, such as in “[el] asma afecta […]”.
-target: indicates who receives the effect of the action, such as in “[…] afecta [las] vías respiratorias”.
+\begin{description}
+  \item[in-time:] to indicate that something exists, occurs or is confined to a time-frame, such as in “exposición” in-time “verano”.
+  \item[in-place:] to indicate that something exists, occurs or is confined to a place or location.
+  \item[in-context:] to indicate a general context in which something happens, like a mode, manner, or state, such as “exposición” in-context “prolongada”.
+\end{description}
+
+\paragraph{Action roles (2):} indicate which role play the entities related to an Action:
+
+\begin{description}
+  \item[subject:] indicates who performs the action, such as in “[el] asma afecta […]”.
+  \item[target:] indicates who receives the effect of the action, such as in “[…] afecta [las] vías respiratorias”.
 Actions can have several subjects and targets, in which case the semantic interpreted is that the union of the subjects performs the action over each of the targets.
-Predicate roles (2): indicate which role play the entities related to a Predicate:
+\end{description}
 
-domain: indicates the main entity on which the predicate applies.
-arg: indicates an additional entity that specifies a value for the predicate to make sense.
+\paragraph{Predicate roles (2):} indicate which role play the entities related to a Predicate:
+
+\begin{description}
+  \item[domain:] indicates the main entity on which the predicate applies.
+  \item[arg:] indicates an additional entity that specifies a value for the predicate to make sense.
 The exact semantic of this argument depends on the semantic of the predicate label, such as in “mayores [de] 60 años”, where the predicate label “mayores” indicates that “60 años” is a quantity, that restricts the minimum age for the predicate to be true.
+\end{description}
 
@@
 -- Fórmulas
-Rec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + M_A + M_B}
+$$Rec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + M_A + M_B}$$
 
-Prec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + S_A + S_B}
+$$Prec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + S_A + S_B}$$
 
-F_{1AB} = 2 \cdot \frac{Prec_{AB} \cdot Rec_{AB}}{Prec_{AB} + Rec_{AB}}
+$$F_{1AB} = 2 \cdot \frac{Prec_{AB} \cdot Rec_{AB}}{Prec_{AB} + Rec_{AB}}$$
 

### 2021-06-19 paper/paper.tex
poniendo citas equipos

@@
 
-  \item[Team GuanZhengy~\cite{guanzhengyi}] presents a traditional NER architecture for Subtask A, based on contextual embeddings from a BETO pre-trained language model, and a combination of Convolutional, Bi-LSTM, and CRF layers for decoding BIO tags.
+  \item[Team GuanZhengy~\cite{GuanZhengyi2021}] presents a traditional NER architecture for Subtask A, based on contextual embeddings from a BETO pre-trained language model, and a combination of Convolutional, Bi-LSTM, and CRF layers for decoding BIO tags.
 
-  \item[Team IXA~\cite{ixa}] models both substasks are sequence labeling problems encoded with a BIO system and using a pre-trained XLM-RoBERTa language model.
+  \item[Team IXA~\cite{edgarandres2021}] models both substasks are sequence labeling problems encoded with a BIO system and using a pre-trained XLM-RoBERTa language model.
 Subtask A is solved with a standard NER architecture.
@@
 
-  \item[Team JAD~\cite{jad}] proposes a single model based on BERT pre-trained embeddings that jointly outputs entity labels~(at token level) and pairwise relation labels.
+  \item[Team JAD~\cite{JAD2021}] proposes a single model based on BERT pre-trained embeddings that jointly outputs entity labels~(at token level) and pairwise relation labels.
 To deal with multi-span entities, they add a virtual relation that links tokens from the same entity.
 
-  \item[Team Maoquin~\cite{maoquin}] presents a traditional NER architecture based on BERT pre-trained embeddings and BIO tags for Subtask A, combined with Bi-LSTM and CRF layers.
+  \item[Team Maoquin~\cite{Maoqin2021}] presents a traditional NER architecture based on BERT pre-trained embeddings and BIO tags for Subtask A, combined with Bi-LSTM and CRF layers.
 
-  \item[Team PUCRJ-PUCPR-UFMG~\cite{pucrj}] proposes a joint model that outputs token labels~(modelled as a sequence labelling problem) and pairwise relation labels, based on BERT pre-trained embeddings as the main feature.
+  \item[Team PUCRJ-PUCPR-UFMG~\cite{PUCRJ-PUCPR-UFMG2021}] proposes a joint model that outputs token labels~(modelled as a sequence labelling problem) and pairwise relation labels, based on BERT pre-trained embeddings as the main feature.
 
-  \item[Team uhKD4~\cite{uhkd4}] models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
+  \item[Team uhKD4~\cite{uhKD42021}] models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
 As features, they employ a variety of syntactic characteristics~(POS-tags, character embeddings, positional embeddings) as well as word2vec embeddings.
 
-  \item[Team UH-MMM~\cite{uhmmm}] also models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
+  \item[Team UH-MMM~\cite{uh-mmm2021}] also models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
 As a key characteristic, they encode the shortest dependency path between two entities for the relation predction.
@@
 
-  \item[Team Vicomtech~\cite{vicomtech}] presents two different models.
+  \item[Team Vicomtech~\cite{vicomtech2021}] presents two different models.
 The first consists of a joint architecture for sequence labelling~(Subtask A) and pairwise relation prediciton~(Subtask B) based on BERT pre-trained embeddings.

### 2021-06-19 paper/paper.tex
Update

--- 2021-06-19 paper/paper.tex
@@
 \usepackage{tabularx}
+\usepackage{todonotes}
 % \usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}
@@
 
-Given a list of eHealth documents written in Spanish, the goal of this subtask is to identify all the entities per document and their types.
+The goal of this subtask is to identify all the entities per document and their types.
 These entities are all the relevant terms (single word or multiple words) that represent semantically important elements in a sentence.
-The following figure shows the relevant entities that appear in a set of example sentences.
-
-Entities will always consist of one or more complete words (i.e., not a prefix or a suffix of a word), and will never include any surrounding punctuation symbols, parenthesis, etc.
+Entities always consist of one or more complete words (i.e., not a prefix or a suffix of a word), and never include any surrounding punctuation symbols, parenthesis, etc.
 There are four types for entities:
@@
 \begin{description}
-  \item[Concept:] indentifies a relevant term, concept, idea, in the knowledge domain of the sentence.
+  \item[Concept:] indentifies a rel willevant term, concept, idea, in the knowledge domain of the sentence.
   \item[Action:] indentifies a process or modification of other entities.
@@
 The purpose of this subtask is to recognize all relevant semantic relationships between the entities recognized.
-
 The semantic relations are divided in different categories:
 
-\paragraph{General relations (6)}: general-purpose relations between two concepts (it involves Concept, Action, Predicate, and Reference) that have a specific semantic.
+\paragraph{General relations (6)} are general-purpose relations between two concepts (it involves Concept, Action, Predicate, and Reference) that have a specific semantic.
 When any of these relations applies, it is preferred over a domain relation –tagging a key phrase as a link between two information units–, since their semantic is independent of any textual label:
@@
 
-\paragraph{Contextual relations (3)}: allow to refine an entity (it involves Concept, Action, Predicate, and Reference) by attaching modifiers. These are:
+\paragraph{Contextual relations (3)} allow to refine an entity (it involves Concept, Action, Predicate, and Reference) by attaching modifiers. These are:
 
@@
 
-\paragraph{Action roles (2):} indicate which role play the entities related to an Action:
+\paragraph{Action roles (2)} indicate which role play the entities related to an Action:
 
@@
 
-\paragraph{Predicate roles (2):} indicate which role play the entities related to a Predicate:
+\paragraph{Predicate roles (2)} indicate which role play the entities related to a Predicate:
 
@@
 
-To evaluate each subtask, we count correct, incorrect, partial, missing, and spurious
+To evaluate each subtask, we score correct, incorrect, partial, missing, and spurious
 annotations, and weight them according to an $F_1$ measure, independently per task.
-Partial annotations~(i.e., where predicted entities overlap with the gold standard) are counted as half the value of correct annotations.
+Partial annotations~(i.e., where predicted entities overlap with the gold standard) are scored as half the value of correct annotations.
 
--- Fórmulas
-$$Rec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + M_A + M_B}$$
+$$Rec = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + M_A + M_B}$$
 
-$$Prec_{AB} = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + S_A + S_B}$$
+$$Prec = \frac{C_A + C_B + \frac{1}{2} P_A}{C_A + I_A + C_B + P_A + S_A + S_B}$$
 
-$$F_{1AB} = 2 \cdot \frac{Prec_{AB} \cdot Rec_{AB}}{Prec_{AB} + Rec_{AB}}$$
+$$F_1 = 2 \cdot \frac{Prec \cdot Rec}{Prec + Rec}$$
 
 Furthermore, the challenge is graded in three different scenarios:
-one for each subtask and one where both subtasks are performed in sequence.
-This is the main scenario, which ultimately decides the winner of the challenge,
-although all other results are interesting.
+one scenario for each subtask independently, and a main scenario where both subtasks are performed in sequence, which ultimately decides the winner of the challenge.
+In the subtask-specific scenarios, the previous formulas are redefined based only on the relevant subset of annotations for each subtask.
 
@@
 and newly annotated sentences.
-
-For the eHealth-KD 2021 edition, systems will be evaluated in a cross-domain and multi-language corpus.
-Both the training, development, and test collections will contain sentences extracted from MedlinePlus, Wikinews, and the CORD-19 corpus,
-all of them related with health topics, but showing a significant variety in terms of format and structure.
+The corpus is divided into three collections: training, development, and testing.
+All collections contain sentences extracted from MedlinePlus, Wikinews, and the CORD-19 corpus, related with health topics, but showing a significant variety in terms of format and structure.
 Furthermore, the majority of sentences are in Spanish, but a small set of English sentences is also included, to evaluate generalization across domains.
 
-In the training collection, each sentence will be labeled with its corresponding domain and language (Spanish or English),
-so that participants can potentially fine-tune different models for each domain/language and learn to identify them in the text.
-In the development collection, sentences will be mixed from all different sources and no labelling will be provided,
-so that participants can evaluate their systems in a similar environment to the testing set.
+In the training collection, each sentence is labeled with its corresponding domain and language (Spanish or English), so that participants can potentially fine-tune different models for each domain/language and learn to identify them in the text.
+In the development collection, sentences are from all different sources and no labelling is provided, so that participants can evaluate their systems in a similar environment to the testing set.
+In the testing set, a large number of unlabelled sentences is added along with a small batch of labelled sentences. This serves to discourage participants from manually labelling the test set.
 
-Participants can opt-out of the cross-domain / multi-language challenge at evaluation time,
-in which case only the metrics from the main domain (MedlinePlus) and language (Spanish) will be used.
-
-As in the previous edition, the corpus for eHealth-KD 2021 will use a corpus extracted from MedlinePlus sources, plus additional resources.
+As in previous edition, the corpus for eHealth-KD 2021 is based mostly on text extracted from MedlinePlus sources, plus additional resources.
 First, the same corpus used in the 2020 edition will be provided for training and development, while a new set of previously unlabelled sentences will be manually annotated and used for the test collection.
 Additionally, health-related news sourced from Wikinews will be also provided for training and development.
-Finally, a small set of sentences from scientific papers in the CORD-19 corpus (in English language) will be selected, annotated, and distributed in the development, and testing collections.
-
-%Three different sources of textual information are sampled: medline articles,
-%wikinews articles, and biomedical papers from the CORD-19 corpus.
-
-The corpus will be divided into three sections. Training and development sets are published along with baseline implementations,
-for participants to train and fine-tune their systems. These files consist of both plain text input and the expected outputs for both subtasks.
-
-%The medline and wikinews articles are in Spanish, while CORD are in English.
-
-From the 2019 and 2020 challenges, X sentences where taken.
-
-For this new edition, Y sentences were annotated by a team of annotators.
-The team composition is 4 junior annotators and 3 senior annotators.
-2 junior annotators annotated each sentence, and a senior annotator performed the merging.
-
-The newly annotated sentences are used solely for evaluation purposes,
-while all training and development resources are reused from previous challenges.
-
-contains 3000 sentences. The first 2700 are in Spanish and the last 300 are in English. Of these, only 50 in each language will
-be used for evaluation (the rest are provided to discourage manual annotation), but you must output annotations for all of the sentences,
-since the reference sentences are shuffled.
-
+Finally, a small set of sentences from scientific papers in the CORD-19 corpus (in English language) are selected, annotated, and distributed in the development, and testing collections.
 Overall, the composition of the corpus is presented in Table~\ref{tab:corpus}.
 
-\begin{table}
+\todo{llenar tabla}
+
+\begin{table*}
   \caption{Composition of the corpus, highlighting resources from previous
   challenges and newly annotated sentences.\label{tab:corpus}}
-\end{table}
+\end{table*}
 

### 2021-06-19 paper/paper.tex
Bibtex

--- 2021-06-19 paper/paper.tex
@@
 
-  \item[Team GuanZhengy~\cite{guanzhengyi}] presents a traditional NER architecture for Subtask A, based on contextual embeddings from a BETO pre-trained language model, and a combination of Convolutional, Bi-LSTM, and CRF layers for decoding BIO tags.
+  \item[Team GuanZhengy] presents a traditional NER architecture for Subtask A, based on contextual embeddings from a BETO pre-trained language model, and a combination of Convolutional, Bi-LSTM, and CRF layers for decoding BIO tags~\cite{GuanZhengyi2021}.
 
-  \item[Team IXA~\cite{ixa}] models both substasks are sequence labeling problems encoded with a BIO system and using a pre-trained XLM-RoBERTa language model.
+  \item[Team IXA] models both substasks are sequence labeling problems encoded with a BIO system and using a pre-trained XLM-RoBERTa language model.
 Subtask A is solved with a standard NER architecture.
-For Subtask B, they solve a sequence labelling problem for each pair of entities, where tags correspond to relation labels.
+For Subtask B, they solve a sequence labelling problem for each pair of entities, where tags correspond to relation labels~\cite{edgarandres2021}.
 
-  \item[Team JAD~\cite{jad}] proposes a single model based on BERT pre-trained embeddings that jointly outputs entity labels~(at token level) and pairwise relation labels.
-To deal with multi-span entities, they add a virtual relation that links tokens from the same entity.
+  \item[Team JAD] proposes a single model based on BERT pre-trained embeddings that jointly outputs entity labels~(at token level) and pairwise relation labels.
+To deal with multi-span entities, they add a virtual relation that links tokens from the same entity~\cite{JAD2021}.
 
-  \item[Team Maoquin~\cite{maoquin}] presents a traditional NER architecture based on BERT pre-trained embeddings and BIO tags for Subtask A, combined with Bi-LSTM and CRF layers.
+  \item[Team Maoquin] presents a traditional NER architecture based on BERT pre-trained embeddings and BIO tags for Subtask A, combined with Bi-LSTM and CRF layers~\cite{Maoqin2021}.
 
-  \item[Team PUCRJ-PUCPR-UFMG~\cite{pucrj}] proposes a joint model that outputs token labels~(modelled as a sequence labelling problem) and pairwise relation labels, based on BERT pre-trained embeddings as the main feature.
+  \item[Team PUCRJ-PUCPR-UFMG] proposes a joint model that outputs token labels~(modelled as a sequence labelling problem) and pairwise relation labels, based on BERT pre-trained embeddings as the main feature~\cite{lucas2021}.
 
-  \item[Team uhKD4~\cite{uhkd4}] models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
-As features, they employ a variety of syntactic characteristics~(POS-tags, character embeddings, positional embeddings) as well as word2vec embeddings.
+  \item[Team uhKD4] models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
+As features, they employ a variety of syntactic characteristics~(POS-tags, character embeddings, positional embeddings) as well as word2vec embeddings~\cite{uhKD42021}.
 
-  \item[Team UH-MMM~\cite{uhmmm}] also models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
+  \item[Team UH-MMM] also models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
 As a key characteristic, they encode the shortest dependency path between two entities for the relation predction.
-They also compare several different embeddings, including health-specific and general-purpose approaches.
+They also compare several different embeddings, including health-specific and general-purpose approaches~\cite{uhmmm2021}.
 
-  \item[Team Vicomtech~\cite{vicomtech}] presents two different models.
+  \item[Team Vicomtech] presents two different models.
 The first consists of a joint architecture for sequence labelling~(Subtask A) and pairwise relation prediciton~(Subtask B) based on BERT pre-trained embeddings.
-The second model is a text-to-text architecture, based on a T5 model, finetunned on a problem-specific encoding of the entities and relations that solves both subtasks in a single pass.
+The second model is a text-to-text architecture, based on a T5 model, finetunned on a problem-specific encoding of the entities and relations that solves both subtasks in a single pass~\cite{vicomtech2021}.
 \end{description}
 
--- Describir ideas generales más usadas
-
-How can see in the table \ref{} BERT and variants predominate as feature extractor although
-some teams add clasic NLP featuures.
+How can see in the Table~\ref{tab:participants} BERT and variants  predominate as feature extractor although some teams add clasic NLP featuures.
 In contrast with previus years the join aproche is used by more than the half of system that present in the involve task
@@
 
-Two approaches break this treads IXA and VICONTECH, The fisrt model the task B
+Two approaches break this treads IXA and VICOMTECH, The first model the task B
 also as sequence labeling reusing the same arquitecture that subtask A.

### 2021-06-19 paper/paper.tex
Update

@@
 
+\begin{figure*}[htb]
+  \includegraphics[width=\textwidth]{model.png}
+  \caption{Examples the annotation model defined for the eHealth-KD Challenge.\label{fig:model}}
+\end{figure*}
+
 The eHealth-KD challenge consists on the automatic sentence-level annotation
 of multi-token entities and binary relations among them.
-
 A custom annotation model has been defined, comprising 4 entity types and 13 relations,
@@
 The challenge has been divided into two different subtasks: entity recognition and relation extraction.
-
-\begin{figure*}
-  \includegraphics[width=\textwidth]{model.png}
-  \caption{Examples the annotation model defined for the eHealth-KD Challenge.\label{fig:model}}
-\end{figure*}
 
@@
 %-- Describir los sistemas
-\begin{description}
-  \item[Team Codestrange] proposes
+  \paragraph{Codestrange} proposes
 
-  \item[Team GuanZhengy] presents a traditional NER architecture for Subtask A, based on contextual embeddings from a BETO pre-trained language model, and a combination of Convolutional, Bi-LSTM, and CRF layers for decoding BIO tags~\cite{GuanZhengyi2021}.
+  \paragraph{GuanZhengy} presents a traditional NER architecture for Subtask A, based on contextual embeddings from a BETO pre-trained language model, and a combination of Convolutional, Bi-LSTM, and CRF layers for decoding BIO tags~\cite{GuanZhengyi2021}.
 
-  \item[Team IXA] models both substasks are sequence labeling problems encoded with a BIO system and using a pre-trained XLM-RoBERTa language model.
+  \paragraph{IXA} models both substasks are sequence labeling problems encoded with a BIO system and using a pre-trained XLM-RoBERTa language model.
 Subtask A is solved with a standard NER architecture.
@@
 
-  \item[Team JAD] proposes a single model based on BERT pre-trained embeddings that jointly outputs entity labels~(at token level) and pairwise relation labels.
+  \paragraph{JAD} proposes a single model based on BERT pre-trained embeddings that jointly outputs entity labels~(at token level) and pairwise relation labels.
 To deal with multi-span entities, they add a virtual relation that links tokens from the same entity~\cite{JAD2021}.
 
-  \item[Team Maoquin] presents a traditional NER architecture based on BERT pre-trained embeddings and BIO tags for Subtask A, combined with Bi-LSTM and CRF layers~\cite{Maoqin2021}.
+  \paragraph{Maoquin} presents a traditional NER architecture based on BERT pre-trained embeddings and BIO tags for Subtask A, combined with Bi-LSTM and CRF layers~\cite{Maoqin2021}.
 
-  \item[Team PUCRJ-PUCPR-UFMG] proposes a joint model that outputs token labels~(modelled as a sequence labelling problem) and pairwise relation labels, based on BERT pre-trained embeddings as the main feature~\cite{lucas2021}.
+  \paragraph{PUCRJ-PUCPR-UFMG} proposes a joint model that outputs token labels~(modelled as a sequence labelling problem) and pairwise relation labels, based on BERT pre-trained embeddings as the main feature~\cite{lucas2021}.
 
-  \item[Team uhKD4] models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
+  \paragraph{uhKD4} models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
 As features, they employ a variety of syntactic characteristics~(POS-tags, character embeddings, positional embeddings) as well as word2vec embeddings~\cite{uhKD42021}.
 
-  \item[Team UH-MMM] also models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
+  \paragraph{UH-MMM} also models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
 As a key characteristic, they encode the shortest dependency path between two entities for the relation predction.
@@
 
-  \item[Team Vicomtech] presents two different models.
+  \paragraph{Vicomtech} presents two different models.
 The first consists of a joint architecture for sequence labelling~(Subtask A) and pairwise relation prediciton~(Subtask B) based on BERT pre-trained embeddings.
 The second model is a text-to-text architecture, based on a T5 model, finetunned on a problem-specific encoding of the entities and relations that solves both subtasks in a single pass~\cite{vicomtech2021}.
-\end{description}
 

### 2021-06-19 paper/paper.tex
Add table
Update table

@@
 
-\todo{llenar tabla}
-
-\begin{table*}
+\begin{table}
+  \begin{tabular}{lllr}
+    \toprule
+    Collection & Source & Language & Size \\
+    \midrule
+    Training & Medline & Spanish & 1200 \\
+             & Wikinews & Spanish & 300 \\
+    \midrule
+    Develop & Medline & Spanish & 25 \\
+            & Wikinews & Spanish & 25 \\
+            & CORD & English & 50 \\
+    \midrule
+    Testing & Medline & Spanish & 75 \\
+            & Wikinews & Spanish & 75 \\
+            & CORD & English & 150 \\
+    \midrule
+    Total   &      &         & 1900 \\
+    \bottomrule
+  \end{tabular}
   \caption{Composition of the corpus, highlighting resources from previous
   challenges and newly annotated sentences.\label{tab:corpus}}
-\end{table*}
+\end{table}
 
@@
   \resizebox{\textwidth}{!}{
-  \begin{tabular}{lccccccccc}
+  \begin{tabular}{l|ccc|ccc|ccc}
     \toprule
-    & \multicolumn{3}{c}{\textbf{Main}} & \multicolumn{3}{c}{\textbf{Task A}} & \multicolumn{3}{c}{\textbf{Task B}} \\
+    & \multicolumn{3}{c|}{\textbf{Main}} & \multicolumn{3}{c|}{\textbf{Task A}} & \multicolumn{3}{c}{\textbf{Task B}} \\
     \textbf{Team}    & $F_1$ & $P$   & $R$   & $F_1$ & $P$   & $R$   & $F_1$ & $P$   & $R$ \\
     \midrule
-    Vicomtech        & 0.531 & 0.540 & 0.534 & 0.684 & 0.699 & 0.747 & 0.371 & 0.541 & 0.283 \\
-    PUCRJ-PUCPR-UFMG & 0.528 & 0.568 & 0.502 & 0.706 & 0.714 & 0.697 & 0.263 & 0.366 & 0.205 \\
-    IXA              & 0.498 & 0.464 & 0.538 & 0.653 & 0.613 & 0.698 & 0.430 & 0.453 & 0.409 \\
+    Vicomtech        & \bf 0.531 & 0.540 & 0.534 & 0.684 & 0.699 & \bf 0.747 & 0.371 & \bf 0.541 & 0.283 \\
+    PUCRJ-PUCPR-UFMG & 0.528 & \bf 0.568 & 0.502 & \bf 0.706 & \bf 0.714 & 0.697 & 0.263 & 0.366 & 0.205 \\
+    IXA              & 0.498 & 0.464 & \bf 0.538 & 0.653 & 0.613 & 0.698 & \bf 0.430 & 0.453 & \bf 0.409 \\
     uhKD4            & 0.422 & 0.485 & 0.374 & 0.527 & 0.517 & 0.537 & 0.317 & 0.556 & 0.222 \\
@@
     Codestrange      & 0.232 & 0.337 & 0.176 & 0.080 & 0.415 & 0.044 & 0.032 & 0.437 & 0.017 \\
-    baseline         & 0.232 & 0.337 & 0.176 & 0.306 & 0.350 & 0.271 & 0.032 & 0.437 & 0.017 \\
+    \it baseline     & 0.232 & 0.337 & 0.176 & 0.306 & 0.350 & 0.271 & 0.032 & 0.437 & 0.017 \\
     JAD              & 0.109 & 0.234 & 0.071 & 0.262 & 0.315 & 0.224 & 0.007 & 0.375 & 0.003 \\
@@
 
-  \caption{Results.\label{tab:results}}
+  \caption{Summary of results in the three evaluation scenarios of the eHealth-KD Challenge. The top result in every metric is highlighted.\label{tab:results}}
 \end{table*}

### 2021-06-20 paper/paper.tex
Update discussion

@@
 
-How can see in the Table~\ref{tab:participants} BERT and variants  predominate as feature extractor although some teams add clasic NLP featuures.
-In contrast with previus years the join aproche is used by more than the half of system that present in the involve task
-Como en años anteriores the subtask A is model as sequens labeling using some variant of BIO encoding.
-Likewise the subtask B is commonly model as pair wise classification.
+As it can be seen in Table~\ref{tab:participants}, the predominant solution for feature extraction is using pre-trained language models such as BERT and its variants, although some approaches also include classic NLP features.
+In contrast with previous editions, the joint approach~(solving both subtasks simultaneously with a shared architecture) is used by more than half of the systems that tackle both subtasks.
+As in previous editions, subtask A is commonly modelled as a sequence labelling problem using some variant of the BIO encoding.
+Likewise, subtask B is commonly modelled as a pairwise classification problem, by combining all pairs of entities detected in each sentence.
 
-Two approaches break this treads IXA and VICOMTECH, The first model the task B
-also as sequence labeling reusing the same arquitecture that subtask A.
-Th second present a arquitecture text to text that translate que raw sentence To
-a semiestructured representation where are encode all the entities and their relations.
+Two approaches stand out as distinctly novel in this edition of the challenge, presented by IXA and Vicomtech, respectively.
+The former models subtask B also as a sequence labelling problem, reusing the same architecture as in subtask A.
+The latter presents a text-to-text architecture which translates a raw sentence into a semi-structured representation that encodes all the entities and their relations.
 
-\section{Challenge Results}\label{sec:results}
+\section{Results and Discussion}\label{sec:results}
 
-Table~\ref{tab:results} summarizes the main results in the challenge.
+Table~\ref{tab:results} summarizes the main results obtained by all participants in the eHealth-KD 2021 Challenge.
+In the main scenario the best performing system was the joint architecture presented by Vicomtech, followed closely by a very similar architecture presented by PUCRJ-PUCPR-UFMG.
+Both approaches are based on the previous edition's winner, further confirming the hypothesis that using end-to-end architectures for solving both subtasks simultaneously outperforms task-specific architectures.
+This advantage seems to be mostly due to the strength of these solutions for solving subtask A, since in subtask B the best performing system is the sequence labelling architecture presented by IXA.
 
@@
 
-In Scenario 1, the best performing system is\dots
+As expected by the relative complexity of the tasks, results for subtask A are significantly better than for subtask B.
+However, neither subtask can be said to be fundamentally solved up to human performance.
+The human benchmark, estimated by inter-annotator agreement, is at least $10$ to $20$ percentual points above the best performing systems in both subtasks, with this gap being larger in subtask B.\todo{estimate human benchmark}
 
--- Describir los demás escenarios
+The use of pre-trained language models seems to provide a significant advantage, taking into consideration the complexities of dealing with multiple domains and languages.
+By leveraging multi-lingual models, most systems are capable of dealing with English sentences even though there is little to no training data~(i.e., only 50 English sentences were annotated in the development).
+However, there is a significant gap in performance across domains and languages, as shown by Table~\ref{tab:models}.\todo{diferencias por dominio y lenguaje}
+This suggests that pre-trained models alone are insuficient as an effective transfer learning method in low-resource scenarios such as the one presented in this challenge.
 
-\section{Discussion}\label{sec:discussion}
+Modelling both subtasks independently seems to be less effective than using some form of shared architecture.
+The three best performing systems exploit in some manner the interrelation between both subtasks, either by using a single architecture with separate outputs~(thus sharing a large part of the feature extraction model), or by reusing the same architecture in both subtasks.
+In contrast, systems that attempt to solve subtask B based on structured information obtained from subtask A have a significant drop in performance in this task.
+This suggests that subtask B also benefits from direct access to the raw sentence, which cannot be effectively captured with position embeddings or dependency subtrees alone.
 
--- Ver los sistemas con sus features y qué features son mejores o peores en cada tarea
+One surprising result is that the best performing system in subtask B uses a sequence labelling approach, as opposed to the most commonly deployed pairwise classification model.
+IXA's approach for subtask B consists in feeding a regular NER architecture~(the same one used for subtask A) with a raw sentence, where two entities of interest are marked.
+The model is trained to output a BIO sequence where tags are aligned with the marked entities and correspond to the label of the relation among them, if any.
+This requires $O(|E|^2)$ queries to the model for each sentence with $|E|$ entities detected.
+We believe this approach can be improved by training the model with all entities at once, predicting one-to-many relations in a single pass, thus reducing the complexity to $O(|E|)$ per sentence.
 
--- Comparar con los baselines en cada tarea, hasta qué nivel está resuelta cada tarea
+A second promising approach for subtask B is presented by Vicomtech, although it didn't obtain competitive enough results.
+This approach consists of a text-to-text architecture, fine-tuned from a T5 language model on the task of translating from raw sentences to a semi-structured output that encodes the result of both subtasks.
+The output structure consists of a list of tuples with all the pairs of entities detected and their corresponding relations.
+However, being a text-to-text model, it suffers from hallucination, which requires some post-processing to fix.
+Furthermore, the output structure still contains unnecessary redundancy~(the same entities need to be predicted for every relation in which they appear).
+However, we believe that this is a fruitful direction for future research that should be explored in greater depth.
 
--- Hablar brevemente de la evolución de los sistemas en las 4 ediciones,
-cómo se han ido moviendo hacia transformers
+Moving towards a full solution to the eHealth-KD challenge, there are some fundamental obstacles that still need to be tackled.
+The most salient one is effectively capturing the interaction between entities and the semantic relations in which they appear.
+As we have learned from observing human annotators, they usually annotate simultaneously entities and relations.
+Furthermore, they do not follow the left-to-right natural order of the sentence, but rather annotate the most salient entities first~(e.g., the main Action and related Concepts) and then add the contextual relations and supporting entities.
+Althought it is unclear whether this strategy is necessary, it presents an interesting alternative approach for designing an automatic annotation system in the form of an agent that performs annotation actions on the sentence, perhaps trained with some reinforced learning approach.
+For this purpose, it could be interesting to analize not only the final annotated sentence but the individual annotation events that human annotators produce, including undoing previous annotations.
 
--- Hablar de la modelación de las entidades y relaciones como tareas separadas,
-la desventaja que puede representar eso porque los sistemas que han ganado hacen
-ambas cosas a la vez, o sea hay representación conjunta que es válida
-
--- Hablar de las relaciones como problema binario, que no tiene en cuenta que ciertas
-relaciones implican posiblemente la aparición de otras.
-
--- hablar de los 2 enfoques raros IXA y Vicomtech, que puede aportar cada uno.
-IXA que lo hacen por cada par de entidades, y se podría hacer para toda la oración a la vez, o al menos para todos los orígenes.
-Vicomtech que tienen problemas con que T5 alucina frases que no están en el texto, que si se podría restringir a output solamente lo que está en la oración original.
-Además que tienen que generar las mismas entidades varias veces, porque hay más relaciones que entidades, una representación más compacta que solo tenga las relaciones puede ayudar.
-
--- Hablar de que el orden en que el humano anota no es el mismo que un sistema,
-y que si se pudiera aprender algo de esto, dar con el dataset no solo las anotaciones
-sino en qué orden fueron realizadas.
-
--- Hablar de la necesidad de cambiar de tareas hacia algo que refleje el valor
-del conocimiento extraído, como question answering.
+The four editions of the eHealth-KD challenge have shown that knowledge discovery in natural language text is still an open and challenging problem.
+Detecting the most relevant entities and relations is but a first step in a hypothetical knowledge discovery system that could be used to intelligently explore the vast amount of information available in natural language.
+Moving up in this pipeline, the next natural step is to create semantic structures~(e.g., knowledge graphs) that integrate the entities and relations detected in a corpus of related sentences.
+This could enable using natural language queries that can be answered with precise factual information encoded in such a semantic structure.
+Future editions of the eHealth-KD challenge will focus on those types of problems, in an attempt to continue fostering research in the full problem of knowledge discovery in natural language.
 

### 2021-06-21 paper/paper.tex
Update from Overleaf

@@
 Staying up-to-date on information about topics of interest is crucial in technical or scientific domains.
-For this purpose, specialists rely on a combination of curated soruces (e.g., domain-specific repositories like arxiv, bioarxiv, semantic scholar) and technologies for search and recommendation (e.g., google scholar).
+For this purpose, specialists rely on a combination of curated sources (e.g., domain-specific repositories like arxiv, bioarxiv, semantic scholar) and technologies for search and recommendation (e.g., google scholar).
 These resources significantly improve the experience of collecting and consuming large amounts of relevant information on a specific topic.
@@
 The first step of this process, i.e., the detection of relevant concepts and semantic relations in text, is already a challenging computational task, given the complexity and variability of natural language.
-To encourage research and development in this area, several academic competitions have been organised through the years by organizations such as CLEF, SEMEVAL, and more recently, IBERLEF.
+To encourage research and development in this area, several academic competitions have been organised through the years by organisations such as CLEF, SEMEVAL, and more recently, IBERLEF.
 
@@
 Two computational tasks are defined: the detection of multi-span, non-contiguous, and potentially overlapping named entities; and the detection of semantic relations between them.
-A shared annotation campaign was organized, where a total of 9 participants presented 10 different systems with varied levels of performance.
+A shared annotation campaign was organised, where a total of 9 participants presented 10 different systems with varied levels of performance.
 
@@
 This setting presents a significant challenge to existing state-of-the-art methods, which often rely on large amounts of training data.
-A succesful approach to the eHealth-KD must leverage transfer learning across different domains and languages, since the vast majority of the training examples are provided in Spanish language and from the Medline domain, while only a small development set is available in the remaining settings.
+A successful approach to the eHealth-KD must leverage transfer learning across different domains and languages, since the vast majority of the training examples are provided in Spanish language and from the Medline domain, while only a small development set is available in the remaining settings.
 With this added complexity, we expect to encourage solutions that can be deployed in low-resource environments, where is unfeasible to train large language models over longs periods of time.
@@
 
-  \paragraph{IXA} models both substasks are sequence labeling problems encoded with a BIO system and using a pre-trained XLM-RoBERTa language model.
+  \paragraph{IXA} models both substasks are sequence labelling problems encoded with a BIO system and using a pre-trained XLM-RoBERTa language model.
 Subtask A is solved with a standard NER architecture.
@@
   \paragraph{UH-MMM} also models both subtasks sequentially, using a standard NER architecture with BILOUV encoding for Subtask A and a pairwise classification model for Subtask B.
-As a key characteristic, they encode the shortest dependency path between two entities for the relation predction.
+As a key characteristic, they encode the shortest dependency path between two entities for the relation prediction.
 They also compare several different embeddings, including health-specific and general-purpose approaches~\cite{uhmmm2021}.
@@
   \paragraph{Vicomtech} presents two different models.
-The first consists of a joint architecture for sequence labelling~(Subtask A) and pairwise relation prediciton~(Subtask B) based on BERT pre-trained embeddings.
-The second model is a text-to-text architecture, based on a T5 model, finetunned on a problem-specific encoding of the entities and relations that solves both subtasks in a single pass~\cite{vicomtech2021}.
+The first consists of a joint architecture for sequence labelling~(Subtask A) and pairwise relation prediction~(Subtask B) based on BERT pre-trained embeddings.
+The second model is a text-to-text architecture, based on a T5 model, fine-tuned on a problem-specific encoding of the entities and relations that solves both subtasks in a single pass~\cite{vicomtech2021}.
 
@@
 However, neither subtask can be said to be fundamentally solved up to human performance.
-The human benchmark, estimated by inter-annotator agreement, is at least $10$ to $20$ percentual points above the best performing systems in both subtasks, with this gap being larger in subtask B.\todo{estimate human benchmark}
+The human benchmark, estimated by inter-annotator agreement, is at least $10$ to $20$ percent points above the best performing systems in both subtasks, with this gap being larger in subtask B.\todo{estimate human benchmark}
 
@@
 However, there is a significant gap in performance across domains and languages, as shown by Table~\ref{tab:models}.\todo{diferencias por dominio y lenguaje}
-This suggests that pre-trained models alone are insuficient as an effective transfer learning method in low-resource scenarios such as the one presented in this challenge.
+This suggests that pre-trained models alone are insufficient as an effective transfer learning method in low-resource scenarios such as the one presented in this challenge.
 
@@
 Furthermore, they do not follow the left-to-right natural order of the sentence, but rather annotate the most salient entities first~(e.g., the main Action and related Concepts) and then add the contextual relations and supporting entities.
-Althought it is unclear whether this strategy is necessary, it presents an interesting alternative approach for designing an automatic annotation system in the form of an agent that performs annotation actions on the sentence, perhaps trained with some reinforced learning approach.
-For this purpose, it could be interesting to analize not only the final annotated sentence but the individual annotation events that human annotators produce, including undoing previous annotations.
+Although it is unclear whether this strategy is necessary, it presents an interesting alternative approach for designing an automatic annotation system in the form of an agent that performs annotation actions on the sentence, perhaps trained with some reinforced learning approach.
+For this purpose, it could be interesting to analyse not only the final annotated sentence but the individual annotation events that human annotators produce, including undoing previous annotations.
 

### 2021-06-22 paper/paper.tex
Update discussion

--- 2021-06-20 paper/paper.tex
@@
 In this context, the eHealth Knowledge Discovery Challenge is designed to foster the development of automatic knowledge discovery systems for natural language sentences in a cross-domain and multi-lingual setting.
-Concretely, a token-level annotation model of 4 entities and 13 semantic relations is defined, and a corpus of more than 1500 sentences from different factual sources~(i.e., Spanish Medline articles, Spanish Wikinews articles, and English biomedical preprints related to COVID-19) is annotated.
-Two computational tasks are defined: the detection of multi-span, non-contiguous, and potentially overlapping named entities; and the detection of semantic relations between them.
+Concretely, a token-level annotation model of 4 entities and 13 semantic relations is defined, and a corpus of more than 1900 sentences from different factual sources~(i.e., Spanish Medline articles, Spanish Wikinews articles, and English biomedical preprints related to COVID-19) is constructed.
+Based on this annotation model, two computational tasks are defined: the detection of multi-span, non-contiguous, and potentially overlapping named entities; and the detection of semantic relations between them.
 A shared annotation campaign was organized, where a total of 9 participants presented 10 different systems with varied levels of performance.
@@
     Codestrange      & 0.232 & 0.337 & 0.176 & 0.080 & 0.415 & 0.044 & 0.032 & 0.437 & 0.017 \\
-    \it baseline     & 0.232 & 0.337 & 0.176 & 0.306 & 0.350 & 0.271 & 0.032 & 0.437 & 0.017 \\
     JAD              & 0.109 & 0.234 & 0.071 & 0.262 & 0.315 & 0.224 & 0.007 & 0.375 & 0.003 \\
@@
     Maoqin           & -     & -     & -     & 0.173 & 0.271 & 0.127 & -     & -     & -     \\
+    \midrule
+    \it human        & 0.644 & 0.673 & 0.618 & 0.831 & 0.862 & 0.802 & 0.621 & 0.596 & 0.647 \\
+    \it baseline     & 0.232 & 0.337 & 0.176 & 0.306 & 0.350 & 0.271 & 0.032 & 0.437 & 0.017 \\
     \bottomrule
@@
 
-  \caption{Summary of results in the three evaluation scenarios of the eHealth-KD Challenge. The top result in every metric is highlighted.\label{tab:results}}
+  \caption{Summary of results in the three evaluation scenarios of the eHealth-KD Challenge.
+The top result in every metric is highlighted.
+For comparative purpose, an estimated \textit{human} performance~(based on inter-annotator agreement) and a simple computational \textit{baseline} are also reported.\label{tab:results}}
 \end{table*}
@@
 However, neither subtask can be said to be fundamentally solved up to human performance.
-The human benchmark, estimated by inter-annotator agreement, is at least $10$ to $20$ percentual points above the best performing systems in both subtasks, with this gap being larger in subtask B.\todo{estimate human benchmark}
+The human benchmark, estimated by inter-annotator agreement, is approximately $11.3$,
+$12.5$, and $19.1$ percent points above the best performing systems in each scenario, respectively.
+This indicates that there is still a significant margin for improvement, especially on the relation extraction subtask.
 
 The use of pre-trained language models seems to provide a significant advantage, taking into consideration the complexities of dealing with multiple domains and languages.
-By leveraging multi-lingual models, most systems are capable of dealing with English sentences even though there is little to no training data~(i.e., only 50 English sentences were annotated in the development).
-However, there is a significant gap in performance across domains and languages, as shown by Table~\ref{tab:models}.\todo{diferencias por dominio y lenguaje}
-This suggests that pre-trained models alone are insuficient as an effective transfer learning method in low-resource scenarios such as the one presented in this challenge.
+By leveraging multi-lingual models, most systems are capable of dealing with English sentences even though there is little to no training data~(i.e., only 50 English sentences were provided in the development collection).
+However, there is a gap in performance across domains and languages, as shown by Table~\ref{tab:models}.
+Most participants have a better performance on the subset of the test collection that corresponds to the \textit{Medline} and \textit{Wikinews} sources, and a correspondingly worse performance on the \textit{CORD} subset.
+On average, performance on \textit{Medline}~(the most common source) is $25.2$ and $15.2$ percent points higher than on \textit{CORD}~(the least common source) for subtask A and B, respectively.
+This suggests that multilingual pre-trained models alone are insuficient as an effective transfer learning method in low-resource scenarios such as the one presented in this challenge.
+
+\begin{table*}
+  \resizebox{\textwidth}{!}{
+  \begin{tabular}{l|rrrr|rrrr|rrrr}
+    \toprule
+    & \multicolumn{4}{c|}{Medline} & \multicolumn{4}{c|}{Wikinews} & \multicolumn{4}{c}{CORD} \\
+    & \multicolumn{2}{c}{Task A} & \multicolumn{2}{c|}{Task B} & \multicolumn{2}{c}{Task A} & \multicolumn{2}{c|}{Task B} & \multicolumn{2}{c}{Task A} & \multicolumn{2}{c}{Task B} \\
+    Team & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff \\
+    \midrule
+Vicomtech        & 0.843 &  0.156 & 0.467 & 0.093 & 0.794 & 0.106 & 0.478 &  0.104 & 0.576 & -0.111 & 0.256 & -0.118 \\
+PUCRJ-PUCPR-UFMG & 0.779 &  0.071 & 0.374 & 0.109 & 0.781 & 0.073 & 0.362 &  0.098 & 0.641 & -0.067 & 0.170 & -0.095 \\
+IXA              & 0.699 &  0.045 & 0.562 & 0.130 & 0.714 & 0.060 & 0.493 &  0.062 & 0.609 & -0.045 & 0.338 & -0.094 \\
+uhKD4            & 0.772 &  0.242 & 0.538 & 0.219 & 0.714 & 0.184 & 0.431 &  0.112 & 0.348 & -0.182 & 0.127 & -0.192 \\
+UH-MMM           & 0.692 &  0.081 & 0.158 & 0.104 & 0.695 & 0.083 & 0.061 &  0.006 & 0.538 & -0.073 & 0.014 & -0.041 \\
+Codestrange      & 0.177 &  0.096 & 0.138 & 0.105 & 0.124 & 0.042 & 0.008 & -0.025 & 0.017 & -0.065 & 0.000 & -0.033 \\
+JAD              & 0.238 & -0.025 & 0.036 & 0.028 & 0.243 & -0.02 & 0.000 & -0.007 & 0.280 &  0.017 & 0.000 & -0.007 \\
+GuanZhengyi      & 0.807 &  0.470 & 0.000 & 0.000 & 0.286 & -0.05 & 0.000 &  0.000 & 0.000 & -0.336 & 0.000 &  0.000 \\
+Maoqin           & 0.266 &  0.094 & 0.000 & 0.000 & 0.269 & 0.097 & 0.000 &  0.000 & 0.000 & -0.172 & 0.000 &  0.000 \\
+    \midrule
+    Average Diff &       &  0.136 &       & 0.087 &       & 0.063 &       &  0.038 &       & -0.114 &       & -0.064 \\
+    \bottomrule
+  \end{tabular}}
+  \caption{Individual results per domain in subtasks A and B.
+The \textit{Diff} column corresponds to the absolute difference between the presented $F_1$ and the aggregated $F_1$ on the corresponding scenario,
+  as reported in Table~\ref{tab:results}. A positive \textit{Diff} indicates that team had a correspondingly better result on that specific subset than in the overall corpus.\label{tab:models}}
+\end{table*}
 
@@
 Furthermore, they do not follow the left-to-right natural order of the sentence, but rather annotate the most salient entities first~(e.g., the main Action and related Concepts) and then add the contextual relations and supporting entities.
-Althought it is unclear whether this strategy is necessary, it presents an interesting alternative approach for designing an automatic annotation system in the form of an agent that performs annotation actions on the sentence, perhaps trained with some reinforced learning approach.
-For this purpose, it could be interesting to analize not only the final annotated sentence but the individual annotation events that human annotators produce, including undoing previous annotations.
+Althought it is unclear whether this strategy is necessary, it presents an interesting alternative approach for designing an automatic annotation system in the form of an agent that performs annotation actions on the sentence, perhaps trained with a reinforcement learning approach.
+For this purpose, it could be interesting to analize not only the final annotated sentence but the individual annotation events that human annotators produce, including the undoing previous annotations.
 

### 2021-06-22 paper/paper.tex
Update

@@
   \item[Action:] indentifies a process or modification of other entities.
-It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition), where it denotes the act of being exposed to the Sun, and “daños” (damages), where it denotes the act of damaging the skin.
-It can also be used to indicate non-verbal functional relations, such as “padre” (parent), etc.
-  \item[Predicate:] identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) with some additional arguments such as “60 años” (60 years).
-  \item[Reference:] identifies a textual element that refers to an entity –of the same sentence or of different one–, which can be indicated by textual clues such as “esta”, “aquel”, etc.
+It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition) and “daños” (damages).
+  \item[Predicate:] identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) withsome additional arguments such as “60 años” (60 years).
+  \item[Reference:] identifies a textual element that refers to an entity --of the same sentence or of different one--, which can be indicated by textual clues such as “esta”, “aquel”, etc.
 \end{description}
@@
 
-\paragraph{General relations (6)} are general-purpose relations between two concepts (it involves Concept, Action, Predicate, and Reference) that have a specific semantic.
-When any of these relations applies, it is preferred over a domain relation –tagging a key phrase as a link between two information units–, since their semantic is independent of any textual label:
+\paragraph{General relations (6)} are general-purpose relations between two entities that have a pre-defined semantic:
 
@@
 
-\paragraph{Contextual relations (3)} allow to refine an entity (it involves Concept, Action, Predicate, and Reference) by attaching modifiers. These are:
+\paragraph{Contextual relations (3)} allow to refine an entity by attaching modifiers:
 
 \begin{description}
-  \item[in-time:] to indicate that something exists, occurs or is confined to a time-frame, such as in “exposición” in-time “verano”.
+  \item[in-time:] to indicate that something exists, occurs or is confined to a time-frame.
   \item[in-place:] to indicate that something exists, occurs or is confined to a place or location.
-  \item[in-context:] to indicate a general context in which something happens, like a mode, manner, or state, such as “exposición” in-context “prolongada”.
+  \item[in-context:] to indicate a general context in which something happens, like a mode, manner, or state.
 \end{description}
@@
 \begin{description}
-  \item[subject:] indicates who performs the action, such as in “[el] asma afecta […]”.
-  \item[target:] indicates who receives the effect of the action, such as in “[…] afecta [las] vías respiratorias”.
-Actions can have several subjects and targets, in which case the semantic interpreted is that the union of the subjects performs the action over each of the targets.
+  \item[subject:] indicates who performs the action.
+  \item[target:] indicates who receives the effect of the action.
 \end{description}
@@
   \item[arg:] indicates an additional entity that specifies a value for the predicate to make sense.
-The exact semantic of this argument depends on the semantic of the predicate label, such as in “mayores [de] 60 años”, where the predicate label “mayores” indicates that “60 años” is a quantity, that restricts the minimum age for the predicate to be true.
 \end{description}
@@
 
-Table~\ref{tab:results} summarizes the main results obtained by all participants in the eHealth-KD 2021 Challenge.
-In the main scenario the best performing system was the joint architecture presented by Vicomtech, followed closely by a very similar architecture presented by PUCRJ-PUCPR-UFMG.
-Both approaches are based on the previous edition's winner, further confirming the hypothesis that using end-to-end architectures for solving both subtasks simultaneously outperforms task-specific architectures.
-This advantage seems to be mostly due to the strength of these solutions for solving subtask A, since in subtask B the best performing system is the sequence labelling architecture presented by IXA.
-
 \begin{table*}
@@
   \end{tabular}}
-
     \caption{Summary of results in the three evaluation scenarios of the eHealth-KD Challenge.
@@
   \end{table*}
+
+Table~\ref{tab:results} summarizes the main results obtained by all participants in the eHealth-KD 2021 Challenge.
+In the main scenario the best performing system was the joint architecture presented by Vicomtech, followed closely by a very similar architecture presented by PUCRJ-PUCPR-UFMG.
+Both approaches are based on the previous edition's winner, further confirming the hypothesis that using end-to-end architectures for solving both subtasks simultaneously outperforms task-specific architectures.
+This advantage seems to be mostly due to the strength of these solutions for solving subtask A, since in subtask B the best performing system is the sequence labelling architecture presented by IXA.
 

### 2021-06-22 paper/paper.tex

@@
 The first step of this process, i.e., the detection of relevant concepts and semantic relations in text, is already a challenging computational task, given the complexity and variability of natural language.
-To encourage research and development in this area, several academic competitions have been organised through the years by organizations such as CLEF, SEMEVAL, and more recently, IBERLEF.
+To encourage research and development in this area, several academic competitions have been organised through the years by organisations such as CLEF, SEMEVAL, and more recently, IBERLEF.
 
 In this context, the eHealth Knowledge Discovery Challenge is designed to foster the development of automatic knowledge discovery systems for natural language sentences in a cross-domain and multi-lingual setting.
-Concretely, a token-level annotation model of 4 entities and 13 semantic relations is defined, and a corpus of more than 1900 sentences from different factual sources~(i.e., Spanish Medline articles, Spanish Wikinews articles, and English biomedical preprints related to COVID-19) is constructed.
-Based on this annotation model, two computational tasks are defined: the detection of multi-span, non-contiguous, and potentially overlapping named entities; and the detection of semantic relations between them.
-A shared annotation campaign was organized, where a total of 9 participants presented 10 different systems with varied levels of performance.
+Concretely, a token-level annotation model of 4 entities and 13 semantic relations is defined, and a corpus of more than 1500 sentences from different factual sources~(i.e., Spanish Medline articles, Spanish Wikinews articles, and English biomedical preprints related to COVID-19) is annotated.
+Two computational tasks are defined: the detection of multi-span, non-contiguous, and potentially overlapping named entities; and the detection of semantic relations between them.
+A shared annotation campaign was organised, where a total of 9 participants presented 10 different systems with varied levels of performance.
 

### 2021-06-22 paper/paper.tex
Updates from Overleaf

@@
   \item[Action:] indentifies a process or modification of other entities.
-It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition) and “daños” (damages).
-  \item[Predicate:] identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) withsome additional arguments such as “60 años” (60 years).
-  \item[Reference:] identifies a textual element that refers to an entity --of the same sentence or of different one--, which can be indicated by textual clues such as “esta”, “aquel”, etc.
+It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition), where it denotes the act of being exposed to the Sun, and “daños” (damages), where it denotes the act of damaging the skin.
+It can also be used to indicate non-verbal functional relations, such as “padre” (parent), etc.
+  \item[Predicate:] identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) with some additional arguments such as “60 años” (60 years).
+  \item[Reference:] identifies a textual element that refers to an entity –of the same sentence or of different one–, which can be indicated by textual clues such as “esta”, “aquel”, etc.
 \end{description}
@@
 
-\paragraph{General relations (6)} are general-purpose relations between two entities that have a pre-defined semantic:
+\paragraph{General relations (6)} are general-purpose relations between two concepts (it involves Concept, Action, Predicate, and Reference) that have a specific semantic.
+When any of these relations applies, it is preferred over a domain relation –tagging a key phrase as a link between two information units–, since their semantic is independent of any textual label:
 
@@
   \item[part-of:] indicates that an entity is a constituent part of another.
-  \item[causes:] indicates that one entity provoques the existence or occurrence of another.
+  \item[causes:] indicates that one entity provokes the existence or occurrence of another.
   \item[entails:] indicates that the existence of one entity implies the existence or occurrence of another.
@@
 
-\paragraph{Contextual relations (3)} allow to refine an entity by attaching modifiers:
+\paragraph{Contextual relations (3)} allow to refine an entity (it involves Concept, Action, Predicate, and Reference) by attaching modifiers. These are:
 
 \begin{description}
-  \item[in-time:] to indicate that something exists, occurs or is confined to a time-frame.
+  \item[in-time:] to indicate that something exists, occurs or is confined to a time-frame, such as in “exposición” in-time “verano”.
   \item[in-place:] to indicate that something exists, occurs or is confined to a place or location.
-  \item[in-context:] to indicate a general context in which something happens, like a mode, manner, or state.
+  \item[in-context:] to indicate a general context in which something happens, like a mode, manner, or state, such as “exposición” in-context “prolongada”.
 \end{description}
@@
 \begin{description}
-  \item[subject:] indicates who performs the action.
-  \item[target:] indicates who receives the effect of the action.
+  \item[subject:] indicates who performs the action, such as in “[el] asma afecta […]”.
+  \item[target:] indicates who receives the effect of the action, such as in “[…] afecta [las] vías respiratorias”.
+Actions can have several subjects and targets, in which case the semantic interpreted is that the union of the subjects performs the action over each of the targets.
 \end{description}
@@
   \item[arg:] indicates an additional entity that specifies a value for the predicate to make sense.
+The exact semantic of this argument depends on the semantic of the predicate label, such as in “mayores [de] 60 años”, where the predicate label “mayores” indicates that “60 años” is a quantity, that restricts the minimum age for the predicate to be true.
 \end{description}
@@
     \toprule
-    Collection & Source & Language & Size \\
+    \textbf{Collection} & \textbf{Source} & \textbf{Language} & \textbf{Size} \\
     \midrule
@@
 
+Table~\ref{tab:results} summarizes the main results obtained by all participants in the eHealth-KD 2021 Challenge.
+In the main scenario the best performing system was the joint architecture presented by Vicomtech, followed closely by a very similar architecture presented by PUCRJ-PUCPR-UFMG.
+Both approaches are based on the previous edition's winner, further confirming the hypothesis that using end-to-end architectures for solving both subtasks simultaneously outperforms task-specific architectures.
+This advantage seems to be mostly due to the strength of these solutions for solving subtask A, since in subtask B the best performing system is the sequence labelling architecture presented by IXA.
+
 \begin{table*}
@@
     Codestrange      & 0.232 & 0.337 & 0.176 & 0.080 & 0.415 & 0.044 & 0.032 & 0.437 & 0.017 \\
+    \it baseline     & 0.232 & 0.337 & 0.176 & 0.306 & 0.350 & 0.271 & 0.032 & 0.437 & 0.017 \\
     JAD              & 0.109 & 0.234 & 0.071 & 0.262 & 0.315 & 0.224 & 0.007 & 0.375 & 0.003 \\
@@
     Maoqin           & -     & -     & -     & 0.173 & 0.271 & 0.127 & -     & -     & -     \\
-    \midrule
-    \it human        & 0.644 & 0.673 & 0.618 & 0.831 & 0.862 & 0.802 & 0.621 & 0.596 & 0.647 \\
-    \it baseline     & 0.232 & 0.337 & 0.176 & 0.306 & 0.350 & 0.271 & 0.032 & 0.437 & 0.017 \\
     \bottomrule
   \end{tabular}}
-    \caption{Summary of results in the three evaluation scenarios of the eHealth-KD Challenge.
-The top result in every metric is highlighted.
-For comparative purpose, an estimated \textit{human} performance~(based on inter-annotator agreement) and a simple computational \textit{baseline} are also reported.\label{tab:results}}
+
+  \caption{Summary of results in the three evaluation scenarios of the eHealth-KD Challenge. The top result in every metric is highlighted.\label{tab:results}}
 \end{table*}
-
-Table~\ref{tab:results} summarizes the main results obtained by all participants in the eHealth-KD 2021 Challenge.
-In the main scenario the best performing system was the joint architecture presented by Vicomtech, followed closely by a very similar architecture presented by PUCRJ-PUCPR-UFMG.
-Both approaches are based on the previous edition's winner, further confirming the hypothesis that using end-to-end architectures for solving both subtasks simultaneously outperforms task-specific architectures.
-This advantage seems to be mostly due to the strength of these solutions for solving subtask A, since in subtask B the best performing system is the sequence labelling architecture presented by IXA.
 
@@
 However, neither subtask can be said to be fundamentally solved up to human performance.
-The human benchmark, estimated by inter-annotator agreement, is approximately $11.3$,
-$12.5$, and $19.1$ percent points above the best performing systems in each scenario, respectively.
-This indicates that there is still a significant margin for improvement, especially on the relation extraction subtask.
+The human benchmark, estimated by inter-annotator agreement, is at least $10$ to $20$ percent points above the best performing systems in both subtasks, with this gap being larger in subtask B.\todo{estimate human benchmark}
 
 The use of pre-trained language models seems to provide a significant advantage, taking into consideration the complexities of dealing with multiple domains and languages.
-By leveraging multi-lingual models, most systems are capable of dealing with English sentences even though there is little to no training data~(i.e., only 50 English sentences were provided in the development collection).
-However, there is a gap in performance across domains and languages, as shown by Table~\ref{tab:models}.
-Most participants have a better performance on the subset of the test collection that corresponds to the \textit{Medline} and \textit{Wikinews} sources, and a correspondingly worse performance on the \textit{CORD} subset.
-On average, performance on \textit{Medline}~(the most common source) is $25.2$ and $15.2$ percent points higher than on \textit{CORD}~(the least common source) for subtask A and B, respectively.
-This suggests that multilingual pre-trained models alone are insuficient as an effective transfer learning method in low-resource scenarios such as the one presented in this challenge.
-
-\begin{table*}
-  \resizebox{\textwidth}{!}{
-  \begin{tabular}{l|rrrr|rrrr|rrrr}
-    \toprule
-    & \multicolumn{4}{c|}{Medline} & \multicolumn{4}{c|}{Wikinews} & \multicolumn{4}{c}{CORD} \\
-    & \multicolumn{2}{c}{Task A} & \multicolumn{2}{c|}{Task B} & \multicolumn{2}{c}{Task A} & \multicolumn{2}{c|}{Task B} & \multicolumn{2}{c}{Task A} & \multicolumn{2}{c}{Task B} \\
-    Team & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff \\
-    \midrule
-Vicomtech        & 0.843 &  0.156 & 0.467 & 0.093 & 0.794 & 0.106 & 0.478 &  0.104 & 0.576 & -0.111 & 0.256 & -0.118 \\
-PUCRJ-PUCPR-UFMG & 0.779 &  0.071 & 0.374 & 0.109 & 0.781 & 0.073 & 0.362 &  0.098 & 0.641 & -0.067 & 0.170 & -0.095 \\
-IXA              & 0.699 &  0.045 & 0.562 & 0.130 & 0.714 & 0.060 & 0.493 &  0.062 & 0.609 & -0.045 & 0.338 & -0.094 \\
-uhKD4            & 0.772 &  0.242 & 0.538 & 0.219 & 0.714 & 0.184 & 0.431 &  0.112 & 0.348 & -0.182 & 0.127 & -0.192 \\
-UH-MMM           & 0.692 &  0.081 & 0.158 & 0.104 & 0.695 & 0.083 & 0.061 &  0.006 & 0.538 & -0.073 & 0.014 & -0.041 \\
-Codestrange      & 0.177 &  0.096 & 0.138 & 0.105 & 0.124 & 0.042 & 0.008 & -0.025 & 0.017 & -0.065 & 0.000 & -0.033 \\
-JAD              & 0.238 & -0.025 & 0.036 & 0.028 & 0.243 & -0.02 & 0.000 & -0.007 & 0.280 &  0.017 & 0.000 & -0.007 \\
-GuanZhengyi      & 0.807 &  0.470 & 0.000 & 0.000 & 0.286 & -0.05 & 0.000 &  0.000 & 0.000 & -0.336 & 0.000 &  0.000 \\
-Maoqin           & 0.266 &  0.094 & 0.000 & 0.000 & 0.269 & 0.097 & 0.000 &  0.000 & 0.000 & -0.172 & 0.000 &  0.000 \\
-    \midrule
-    Average Diff &       &  0.136 &       & 0.087 &       & 0.063 &       &  0.038 &       & -0.114 &       & -0.064 \\
-    \bottomrule
-  \end{tabular}}
-  \caption{Individual results per domain in subtasks A and B.
-The \textit{Diff} column corresponds to the absolute difference between the presented $F_1$ and the aggregated $F_1$ on the corresponding scenario,
-  as reported in Table~\ref{tab:results}. A positive \textit{Diff} indicates that team had a correspondingly better result on that specific subset than in the overall corpus.\label{tab:models}}
-\end{table*}
+By leveraging multi-lingual models, most systems are capable of dealing with English sentences even though there is little to no training data~(i.e., only 50 English sentences were annotated in the development).
+However, there is a significant gap in performance across domains and languages, as shown by Table~\ref{tab:models}.\todo{diferencias por dominio y lenguaje}
+This suggests that pre-trained models alone are insufficient as an effective transfer learning method in low-resource scenarios such as the one presented in this challenge.
 
@@
 Furthermore, they do not follow the left-to-right natural order of the sentence, but rather annotate the most salient entities first~(e.g., the main Action and related Concepts) and then add the contextual relations and supporting entities.
-Althought it is unclear whether this strategy is necessary, it presents an interesting alternative approach for designing an automatic annotation system in the form of an agent that performs annotation actions on the sentence, perhaps trained with a reinforcement learning approach.
-For this purpose, it could be interesting to analize not only the final annotated sentence but the individual annotation events that human annotators produce, including the undoing previous annotations.
+Although it is unclear whether this strategy is necessary, it presents an interesting alternative approach for designing an automatic annotation system in the form of an agent that performs annotation actions on the sentence, perhaps trained with some reinforced learning approach.
+For this purpose, it could be interesting to analyse not only the final annotated sentence but the individual annotation events that human annotators produce, including undoing previous annotations.
 
@@
 
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 

### 2021-06-22 paper/paper.tex
Update from Overleaf

--- 2021-06-22 paper/paper.tex
@@
 that attempts to capture a large part of factual semantics in technical documents,
-including enciclopedias, news, and scientific papers.
+including encyclopedias, news, and scientific papers.
 The annotation model is explained in detail in \namecite{piad2019general}.
@@
 \begin{description}
-  \item[Concept:] indentifies a rel willevant term, concept, idea, in the knowledge domain of the sentence.
-  \item[Action:] indentifies a process or modification of other entities.
+  \item[Concept:] identifies a rel willevant term, concept, idea, in the knowledge domain of the sentence.
+  \item[Action:] identifies a process or modification of other entities.
 It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition) and “daños” (damages).
@@
 Subtask B continues from the output of Subtask A, by linking the entities detected and labelled in the input document.
-The purpose of this subtask is to recognize all relevant semantic relationships between the entities recognized.
+The purpose of this subtask is to recognise all relevant semantic relationships between the entities recognised.
 The semantic relations are divided in different categories:
@@
 All collections contain sentences extracted from MedlinePlus, Wikinews, and the CORD-19 corpus, related with health topics, but showing a significant variety in terms of format and structure.
-Furthermore, the majority of sentences are in Spanish, but a small set of English sentences is also included, to evaluate generalization across domains.
+Furthermore, the majority of sentences are in Spanish, but a small set of English sentences is also included, to evaluate generalisation across domains.
 
-In the training collection, each sentence is labeled with its corresponding domain and language (Spanish or English), so that participants can potentially fine-tune different models for each domain/language and learn to identify them in the text.
+In the training collection, each sentence is labelled with its corresponding domain and language (Spanish or English), so that participants can potentially fine-tune different models for each domain/language and learn to identify them in the text.
 In the development collection, sentences are from all different sources and no labelling is provided, so that participants can evaluate their systems in a similar environment to the testing set.
@@
 
-As in previous edition, the corpus for eHealth-KD 2021 is based mostly on text extracted from MedlinePlus sources, plus additional resources.
+As in previous edition, the corpus for eHealth-KD 2021 is based mostly on text extracted from \textit{Medline} sources, plus additional resources.
 First, the same corpus used in the 2020 edition will be provided for training and development, while a new set of previously unlabelled sentences will be manually annotated and used for the test collection.
-Additionally, health-related news sourced from Wikinews will be also provided for training and development.
-Finally, a small set of sentences from scientific papers in the CORD-19 corpus (in English language) are selected, annotated, and distributed in the development, and testing collections.
+Additionally, health-related news sourced from \textit{Wikinews} will be also provided for training and development.
+Finally, a small set of sentences from scientific papers in the \textit{CORD-19} corpus (in English language) are selected, annotated, and distributed in the development, and testing collections.
 Overall, the composition of the corpus is presented in Table~\ref{tab:corpus}.
@@
     \toprule
-    System & Features & Tasks & Subtask A & Subtask B & Multi-span \\
+    \textbf{System} & \textbf{Features} & \textbf{Tasks} & \textbf{Task A} & \textbf{Task B} & \textbf{Multi-span} \\
     \midrule
@@
 
-Table~\ref{tab:results} summarizes the main results obtained by all participants in the eHealth-KD 2021 Challenge.
+Table~\ref{tab:results} summarises the main results obtained by all participants in the eHealth-KD 2021 Challenge.
 In the main scenario the best performing system was the joint architecture presented by Vicomtech, followed closely by a very similar architecture presented by PUCRJ-PUCPR-UFMG.
@@
 On average, performance on \textit{Medline}~(the most common source) is $25.2$ and $15.2$ percent points higher than on \textit{CORD}~(the least common source) for subtask A and B, respectively.
-This suggests that multilingual pre-trained models alone are insuficient as an effective transfer learning method in low-resource scenarios such as the one presented in this challenge.
+This suggests that multilingual pre-trained models alone are insufficient as an effective transfer learning method in low-resource scenarios such as the one presented in this challenge.
 
@@
     \toprule
-    & \multicolumn{4}{c|}{Medline} & \multicolumn{4}{c|}{Wikinews} & \multicolumn{4}{c}{CORD} \\
-    & \multicolumn{2}{c}{Task A} & \multicolumn{2}{c|}{Task B} & \multicolumn{2}{c}{Task A} & \multicolumn{2}{c|}{Task B} & \multicolumn{2}{c}{Task A} & \multicolumn{2}{c}{Task B} \\
-    Team & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff & $F_1$ & Diff \\
+    & \multicolumn{4}{c|}{\textit{Medline}} & \multicolumn{4}{c|}{\textit{Wikinews}} & \multicolumn{4}{c}{\textit{CORD}} \\
+    & \multicolumn{2}{c}{\textbf{Task A}} & \multicolumn{2}{c|}{\textbf{Task B}} & \multicolumn{2}{c}{\textbf{Task A}} & \multicolumn{2}{c|}{\textbf{Task B}} & \multicolumn{2}{c}{\textbf{Task A}} & \multicolumn{2}{c}{\textbf{Task B}} \\
+    \textbf{Team} & $F_1$ & \textit{Diff} & $F_1$ & \textit{Diff} & $F_1$ & \textit{Diff} & $F_1$ & \textit{Diff} & $F_1$ & \textit{Diff} & $F_1$ & \textit{Diff} \\
     \midrule
@@
     \midrule
-    Average Diff &       &  0.136 &       & 0.087 &       & 0.063 &       &  0.038 &       & -0.114 &       & -0.064 \\
+    Mean difference &       &  0.136 &       & 0.087 &       & 0.063 &       &  0.038 &       & -0.114 &       & -0.064 \\
     \bottomrule

### 2021-06-22 paper/paper.tex
Update authors

@@
 
-\author {\textbf{Nombre Apellidos1,$^1$} \textbf{Nombre Apellidos2$^2$}\\
-$^1$Universidad o lugar de trabajo\\
-$^2$Universidad o lugar de trabajo\\
-Información de contacto\\
+\author {
+  \textbf{Alejandro Piad-Morffis,$^{1,*}$},
+  \textbf{Suilan Estevez-Velarde$^1$},
+  \textbf{Yoan Gutierrez$^{2,3}$}\\
+  \textbf{Yudivian Almeida-Cruz$^1$},
+  \textbf{Andrés Montoyo$^{2,3}$},
+  \textbf{Rafael Muñoz$^{2,3}$}\\
+$^1$School of Math and Computer Science, University of Havana, Cuba\\
+\texttt{\{apiad,sestevez,yudy\}@matcom.uh.cu}\\
+$^2$University Institute for Computer Research, IIUI, University of Alicante, Spain\\
+$^2$Department of Language and Computing Systems, University of Alicante, Spain\\
+\texttt{\{ygutierrez,montoyo,rafael\}@dlsi.ua.es}\\
 }

### 2021-06-22 paper/paper.tex
Add codestrange

@@
     \midrule
-    Codestrange & 				 \\
+    Codestrange & Spacy & Only A & Sequence & - & Custom \\
     GuanZhengyi & BETO & Only A & Sequence & - & BIO \\
@@
 
-%-- Describir los sistemas
-  \paragraph{Codestrange} proposes
+  \paragraph{Codestrange} proposes a stadnard NER pipeline trained with the \texttt{spacy} library, modified to fit the eHealth-KD annotation model.
+They apply some preprocessing steps to deal with multi-token annotations, which are not natively handled by the tool.
 

### 2021-06-22 paper/paper.tex
Add conclusiones

@@
 In this context, the eHealth Knowledge Discovery Challenge is designed to foster the development of automatic knowledge discovery systems for natural language sentences in a cross-domain and multi-lingual setting.
-Concretely, a token-level annotation model of 4 entities and 13 semantic relations is defined, and a corpus of more than 1500 sentences from different factual sources~(i.e., Spanish Medline articles, Spanish Wikinews articles, and English biomedical preprints related to COVID-19) is annotated.
+Concretely, a token-level annotation model of 4 entities and 13 semantic relations is defined, and a corpus of 1800 sentences from different factual sources~(i.e., Spanish Medline articles, Spanish Wikinews articles, and English biomedical preprints related to COVID-19) is annotated.
 Two computational tasks are defined: the detection of multi-span, non-contiguous, and potentially overlapping named entities; and the detection of semantic relations between them.
@@
     \midrule
-    Total   &      &         & 1900 \\
+    Total   &      &         & 1800 \\
     \bottomrule
@@
 
+The eHealth Knowledge Discovery Challenge, in its fourth edition, demonstrated that there is a growing interest in the NLP community, both Spanish-speaking and international, related to research in knowledge discovery in natural language.
+While the top performing solutions are all based on state-of-the-art neural architectures, there is still a large margin for improvement, especially regarding transfer learning to low-resource domains.
+New approaches not based on the standard NER pipeline seem promising, but still require further development before they can be applied successfully in such a challenging scenario.
+
 \section*{Acknowledgements}

### 2021-06-22 paper/paper.tex
Full paper

@@
 
-\setlength\titlebox{4in} %esto por defecto
+\setlength\titlebox{5.5in} %esto por defecto
 
@@
 
-\seplnclave{Palabras, palabras, palabras en castellano...}
+\seplnclave{Reconocimiento de Entidades Nombradas, Extracción de Relaciones, Descubrimiento de Conocimiento, Tarea}
 
-\seplnresumen{Resumen del artículo en castellano con una sangría a izquierda y
-derecha de 1 cm, justificado por ambos lados, con tamaño de fuente
-11.}
+\seplnresumen{Este artículo resume la Tarea de Descubrimiento de Conocimiento en Salud presentada en IberLEF 2021.
+Se describen la tarea, los recursos creados, y los sistemas que participaron.
+Se discuten los resultados principales obtenidos por estos sistemas, y se presentan recomendaciones para continuar la investigación en esta temática.}
 
-\seplnkey{Palabras, palabras, palabras en inglés...}
+\seplnkey{Named Entity Recognition, Relation Extraction, Knowledge Discovery, Challenge}
 
-\seplnabstract{Resumen del artículo en inglés con una sangría a izquierda y
-derecha de 1 cm, justificado por ambos lados, con tamaño de fuente
-11.}
+\seplnabstract{This paper summarises the eHealth Knowledge Discovery Challenge hosted at IberLEF 2021.
+The task, resources, and participating systems are described.
+The main results are highlighted and discussed.
+The best performing systems are analysed, and recommendation for future research are presented.}
 

### 2021-06-22 paper/paper.tex
Add table position
Simplify annotation

@@
   \item[Concept:] identifies a rel willevant term, concept, idea, in the knowledge domain of the sentence.
-  \item[Action:] identifies a process or modification of other entities.
-It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition) and “daños” (damages).
-  \item[Predicate:] identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) withsome additional arguments such as “60 años” (60 years).
-  \item[Reference:] identifies a textual element that refers to an entity --of the same sentence or of different one--, which can be indicated by textual clues such as “esta”, “aquel”, etc.
+  \item[Action:] identifies a process or modification of other entities. It can be indicated by a verb or verbal construction, and also by nouns.
+  \item[Predicate:] identifies a function or filter of another set of elements, which has a semantic label in the text, and is applied to an entity with some additional arguments.
+  \item[Reference:] identifies a textual element that refers to an entity of the same sentence or of different one.
 \end{description}
@@
 
-\begin{table*}[t!]
+\begin{table*}[htb]
   \centering
@@
 
-\begin{table*}
+\begin{table*}[htb]
   \resizebox{\textwidth}{!}{

### 2021-06-22 paper/paper.tex
Updates
Update on Overleaf

@@
 \begin{description}
-  \item[Concept:] identifies a rel willevant term, concept, idea, in the knowledge domain of the sentence.
+  \item[Concept:] identifies a relevant term, concept, idea, in the knowledge domain of the sentence.
   \item[Action:] identifies a process or modification of other entities. It can be indicated by a verb or verbal construction, and also by nouns.
@@
 
-  \paragraph{Codestrange} proposes a stadnard NER pipeline trained with the \texttt{spacy} library, modified to fit the eHealth-KD annotation model.
-They apply some preprocessing steps to deal with multi-token annotations, which are not natively handled by the tool.
+  \paragraph{Codestrange} proposes a standard NER pipeline trained with the \texttt{spacy} library, modified to fit the eHealth-KD annotation model.
+They apply some preprocessing steps to deal with multi-token annotations, which are not handled automatically by the tool.
 
@@
 
+\todo[inline]{Comentar GuanZengyi con respecto a la complejidad del transfer learning...}
+
 \begin{table*}[htb]
@@
     \midrule
-Vicomtech        & 0.843 &  0.156 & 0.467 & 0.093 & 0.794 & 0.106 & 0.478 &  0.104 & 0.576 & -0.111 & 0.256 & -0.118 \\
-PUCRJ-PUCPR-UFMG & 0.779 &  0.071 & 0.374 & 0.109 & 0.781 & 0.073 & 0.362 &  0.098 & 0.641 & -0.067 & 0.170 & -0.095 \\
-IXA              & 0.699 &  0.045 & 0.562 & 0.130 & 0.714 & 0.060 & 0.493 &  0.062 & 0.609 & -0.045 & 0.338 & -0.094 \\
+Vicomtech        & \bf 0.843 &  0.156 & 0.467 & 0.093 & \bf 0.794 & 0.106 & 0.478 &  0.104 & 0.576 & -0.111 & 0.256 & -0.118 \\
+PUCRJ-PUCPR-UFMG & 0.779 &  0.071 & 0.374 & 0.109 & 0.781 & 0.073 & 0.362 &  0.098 & \bf 0.641 & -0.067 & 0.170 & -0.095 \\
+IXA              & 0.699 &  0.045 & \bf 0.562 & 0.130 & 0.714 & 0.060 & \bf 0.493 &  0.062 & 0.609 & -0.045 & \bf 0.338 & -0.094 \\
 uhKD4            & 0.772 &  0.242 & 0.538 & 0.219 & 0.714 & 0.184 & 0.431 &  0.112 & 0.348 & -0.182 & 0.127 & -0.192 \\
@@
 \end{table*}
+
+\todo[inline]{Grafica de lineas para ver la evolucion del transferlearning entre diminios}
 
@@
 Furthermore, they do not follow the left-to-right natural order of the sentence, but rather annotate the most salient entities first~(e.g., the main Action and related Concepts) and then add the contextual relations and supporting entities.
-Althought it is unclear whether this strategy is necessary, it presents an interesting alternative approach for designing an automatic annotation system in the form of an agent that performs annotation actions on the sentence, perhaps trained with a reinforcement learning approach.
-For this purpose, it could be interesting to analize not only the final annotated sentence but the individual annotation events that human annotators produce, including the undoing previous annotations.
+Although it is unclear whether this strategy is necessary, it presents an interesting alternative approach for designing an automatic annotation system in the form of an agent that performs annotation actions on the sentence, perhaps trained with a reinforcement learning approach.
+For this purpose, it could be interesting to analyse not only the final annotated sentence but the individual annotation events that human annotators produce, including the undoing previous annotations.
 
@@
 
+\todo[inline]{Grafica de dispersion dificultad para identificar cada tipo de etiqueta}
+
 \section{Conclusions}\label{sec:conclusions}
@@
 
+\todo[inline]{Hablar del aporte de la tarea}
+
 \section*{Acknowledgements}
+This research has been supported by a Carolina Foundation grant in agreement with University of Alicante and University of Havana.
+Moreover, the research has been partially funded by the University of Alicante and the University of Havana, the Generalitat Valenciana (\textit{Conselleria d’Educació, Investigació, Cultura i Esport}) and the Spanish Government through the projects LIVING-LANG (RTI2018-094653-B-C22), INTEGER (RTI2018-094649-B-I00)  and SIIA (PROMETEO/2018/089, PROMETEU/2018/089).
+Additionally, it has been backed by the work of both COST Actions: \texttt{CA19134} -- \textit{``Distributed Knowledge Graphs''} and \texttt{CA19142} -- \textit{``Leading Platform for European Citizens, Industries, Academia and Policymakers in Media Accessibility''}.
 

### 2021-06-28 paper/paper.tex
Update from Overleaf

@@
 These resources significantly improve the experience of collecting and consuming large amounts of relevant information on a specific topic.
-Tools like Connected Papers~\cite{} and Papers with Code~\cite{} are one step beyond the indexing of documents, providing summarised and structured representations of the content in a collection of documents.
+Tools like Connected Papers\footnote{\url{https://www.connectedpapers.com/}} and Papers with Code\footnote{\url{https://paperswithcode.com/}} are one step beyond the indexing of documents, providing summarised and structured representations of the content in a collection of documents.
 However, it remains an open problem to automatically combine, summarise, and present the relevant information in a collection of documents in a semantic structure~(e.g., a knowledge graph) that allows a specialist to quickly grasp the essential concepts of a specific knowledge field.
@@
 Section~\ref{sec:systems} describes the different systems presented in the challenge and summarises the main approaches and most common characteristics they share.
-Section~\ref{sec:results} presents the main results of the challenge.
-Section~\ref{sec:discussion} discusses the most interesting insights of the challenge and highlights both the most relevant lessons learned and potential improvements for future similar endeavours.
+Section~\ref{sec:results} presents the main results of the challenge and discusses the most interesting insights of the challenge and highlights both the most relevant lessons learned and potential improvements for future similar endeavours.
 
@@
 
-The eHealth-KD challenge consists on the automatic sentence-level annotation
+The eHealth-KD challenge\footnote{\url{https://ehealthkd.github.io/2021/}} consists on the automatic sentence-level annotation
 of multi-token entities and binary relations among them.
@@
 
-To evaluate each subtask, we score correct, incorrect, partial, missing, and spurious
-annotations, and weight them according to an $F_1$ measure, independently per task.
+To evaluate each subtask, we score correct (C), incorrect(I), partial(P), missing(M), and spurious (S)
+annotations, and weight them according to an $F_1$ measure, independently per subtask, A or B.
 Partial annotations~(i.e., where predicted entities overlap with the gold standard) are scored as half the value of correct annotations.
@@
 Finally, a small set of sentences from scientific papers in the \textit{CORD-19} corpus (in English language) are selected, annotated, and distributed in the development, and testing collections.
-Overall, the composition of the corpus is presented in Table~\ref{tab:corpus}.
+Overall, the composition of the corpus is presented in Table~\ref{tab:corpus}\footnote{\url{https://ehealthkd.github.io/2021/resources}}.
 

### 2021-06-28 paper/paper.tex
Add transfer

@@
 \usepackage{todonotes}
+\usepackage{url}
+
 % \usepackage[spanish,es-nosectiondot, es-tabla, es-noindentfirst, es-nolists]{babel}
@@
 \seplnabstract{This paper summarises the eHealth Knowledge Discovery Challenge hosted at IberLEF 2021.
-The task, resources, and participating systems are described.
-The main results are highlighted and discussed.
-The best performing systems are analysed, and recommendation for future research are presented.}
+We describe the task, resources, and participating systems, highlighting and discussing the main results achieved in the challenge.
+We analyse the best performing systems and present recommendations for future research.}
 
@@
 Furthermore, the majority of sentences are in Spanish, but a small set of English sentences is also included, to evaluate generalisation across domains.
+The corpus with both annotated files in ANN format and ready-to-use files for training and evaluation is available online\footnote{\url{https://github.com/ehealthkd/corpora}}.
 
@@
 Finally, a small set of sentences from scientific papers in the \textit{CORD-19} corpus (in English language) are selected, annotated, and distributed in the development, and testing collections.
-Overall, the composition of the corpus is presented in Table~\ref{tab:corpus}\footnote{\url{https://ehealthkd.github.io/2021/resources}}.
+Overall, the composition of the corpus is presented in Table~\ref{tab:corpus}.
 
@@
 
-As it can be seen in Table~\ref{tab:participants}, the predominant solution for feature extraction is using pre-trained language models such as BERT and its variants, although some approaches also include classic NLP features.
-In contrast with previous editions, the joint approach~(solving both subtasks simultaneously with a shared architecture) is used by more than half of the systems that tackle both subtasks.
-As in previous editions, subtask A is commonly modelled as a sequence labelling problem using some variant of the BIO encoding.
-Likewise, subtask B is commonly modelled as a pairwise classification problem, by combining all pairs of entities detected in each sentence.
-
-Two approaches stand out as distinctly novel in this edition of the challenge, presented by IXA and Vicomtech, respectively.
-The former models subtask B also as a sequence labelling problem, reusing the same architecture as in subtask A.
-The latter presents a text-to-text architecture which translates a raw sentence into a semi-structured representation that encodes all the entities and their relations.
-
-\section{Results and Discussion}\label{sec:results}
-
 \begin{table*}[htb]
@@
 
-Table~\ref{tab:results} summarises the main results obtained by all participants in the eHealth-KD 2021 Challenge.
-In the main scenario the best performing system was the joint architecture presented by Vicomtech, followed closely by a very similar architecture presented by PUCRJ-PUCPR-UFMG.
-Both approaches are based on the previous edition's winner, further confirming the hypothesis that using end-to-end architectures for solving both subtasks simultaneously outperforms task-specific architectures.
-This advantage seems to be mostly due to the strength of these solutions for solving subtask A, since in subtask B the best performing system is the sequence labelling architecture presented by IXA.
+As it can be seen in Table~\ref{tab:participants}, the predominant solution for feature extraction is using pre-trained language models such as BERT and its variants, although some approaches also include classic NLP features.
+In contrast with previous editions, the joint approach~(solving both subtasks simultaneously with a shared architecture) is used by more than half of the systems that tackle both subtasks.
+As in previous editions, subtask A is commonly modelled as a sequence labelling problem using some variant of the BIO encoding.
+Likewise, subtask B is commonly modelled as a pairwise classification problem, by combining all pairs of entities detected in each sentence.
 
-As expected by the relative complexity of the tasks, results for subtask A are significantly better than for subtask B.
-However, neither subtask can be said to be fundamentally solved up to human performance.
-The human benchmark, estimated by inter-annotator agreement, is approximately $11.3$,
-$12.5$, and $19.1$ percent points above the best performing systems in each scenario, respectively.
-This indicates that there is still a significant margin for improvement, especially on the relation extraction subtask.
+Two approaches stand out as distinctly novel in this edition of the challenge, presented by IXA and Vicomtech, respectively.
+The former models subtask B also as a sequence labelling problem, reusing the same architecture as in subtask A.
+The latter presents a text-to-text architecture which translates a raw sentence into a semi-structured representation that encodes all the entities and their relations.
 
-The use of pre-trained language models seems to provide a significant advantage, taking into consideration the complexities of dealing with multiple domains and languages.
-By leveraging multi-lingual models, most systems are capable of dealing with English sentences even though there is little to no training data~(i.e., only 50 English sentences were provided in the development collection).
-However, there is a gap in performance across domains and languages, as shown by Table~\ref{tab:models}.
-Most participants have a better performance on the subset of the test collection that corresponds to the \textit{Medline} and \textit{Wikinews} sources, and a correspondingly worse performance on the \textit{CORD} subset.
-On average, performance on \textit{Medline}~(the most common source) is $25.2$ and $15.2$ percent points higher than on \textit{CORD}~(the least common source) for subtask A and B, respectively.
-This suggests that multilingual pre-trained models alone are insufficient as an effective transfer learning method in low-resource scenarios such as the one presented in this challenge.
-
-\todo[inline]{Comentar GuanZengyi con respecto a la complejidad del transfer learning...}
+\section{Results and Discussion}\label{sec:results}
 
@@
 
-\todo[inline]{Grafica de lineas para ver la evolucion del transferlearning entre diminios}
+Table~\ref{tab:results} summarises the main results obtained by all participants in the eHealth-KD 2021 Challenge.
+In the main scenario the best performing system was the joint architecture presented by Vicomtech, followed closely by a very similar architecture presented by PUCRJ-PUCPR-UFMG.
+Both approaches are based on the previous edition's winner, further confirming the hypothesis that using end-to-end architectures for solving both subtasks simultaneously outperforms task-specific architectures.
+This advantage seems to be mostly due to the strength of these solutions for solving subtask A, since in subtask B the best performing system is the sequence labelling architecture presented by IXA.
+
+As expected by the relative complexity of the tasks, results for subtask A are significantly better than for subtask B.
+However, neither subtask can be said to be fundamentally solved up to human performance.
+The human benchmark, estimated by inter-annotator agreement, is approximately $11.3$,
+$12.5$, and $19.1$ percent points above the best performing systems in each scenario, respectively.
+This indicates that there is still a significant margin for improvement, especially on the relation extraction subtask.
+
+The use of pre-trained language models seems to provide a significant advantage, taking into consideration the complexities of dealing with multiple domains and languages.
+By leveraging multi-lingual models, most systems are capable of dealing with English sentences even though there is little to no training data~(i.e., only 50 English sentences were provided in the development collection).
+However, there is a gap in performance across domains and languages, as shown by Table~\ref{tab:models}.
+Most participants have a better performance on the subset of the test collection that corresponds to the \textit{Medline} and \textit{Wikinews} sources, and a correspondingly worse performance on the \textit{CORD} subset.
+On average, performance on \textit{Medline}~(the most common source) is $25.2$ and $15.2$ percent points higher than on \textit{CORD}~(the least common source) for subtask A and B, respectively.
+This suggests that multilingual pre-trained models alone are insufficient as an effective transfer learning method in low-resource scenarios such as the one presented in this challenge.
+
+Figure~\ref{fig:transfer} represents the performance for each team across different subset collections of the testing set.
+As it can be observed, most teams present a significant drop in performance, in both subtasks, for the CORD subset with respect to the Medline and the Wikinews subsets.
+This highlights the relative difficulty of the transfer learning component of the challenge.
+IXA presented the most robust system in this respect.
+As an illustrative example, the system presented by GuanZengyi obtained the second best results on the Medline subset of the testing collection, but their performance drops sharply in the remaining subsets, hence achieving an overall score marginally superior to the baseline.
+
+\begin{figure*}
+  \includegraphics[width=\textwidth]{transfer.png}
+  \caption{Graphical representation of the performance by team in each subset collection of the testing set.
+Each bar represents the scores obtained by each team in both subtasks in a specific subset collection.\label{fig:transfer}}
+\end{figure*}
 
@@
 
-Moving towards a full solution to the eHealth-KD challenge, there are some fundamental obstacles that still need to be tackled.
+Moving towards a full solution for the eHealth-KD challenge, there are some fundamental obstacles that still need to be tackled.
 The most salient one is effectively capturing the interaction between entities and the semantic relations in which they appear.
-As we have learned from observing human annotators, they usually annotate simultaneously entities and relations.
+As we have learned from observing human annotators, they usually annotate entities and relations simultaneously.
 Furthermore, they do not follow the left-to-right natural order of the sentence, but rather annotate the most salient entities first~(e.g., the main Action and related Concepts) and then add the contextual relations and supporting entities.
@@
 This research has been supported by a Carolina Foundation grant in agreement with University of Alicante and University of Havana.
-Moreover, the research has been partially funded by the University of Alicante and the University of Havana, the Generalitat Valenciana (\textit{Conselleria d’Educació, Investigació, Cultura i Esport}) and the Spanish Government through the projects LIVING-LANG (RTI2018-094653-B-C22), INTEGER (RTI2018-094649-B-I00)  and SIIA (PROMETEO/2018/089, PROMETEU/2018/089).
+Moreover, the research has been partially funded by the University of Alicante and the University of Havana, the Generalitat Valenciana (\textit{Conselleria d’Educació, Investigació, Cultura i Esport}) and the Spanish Government through the projects LIVING-LANG (\texttt{RTI2018-094653-B-C22}), INTEGER (\texttt{RTI2018-094649-B-I00})  and SIIA (\texttt{PROMETEO/2018/089}, \texttt{PROMETEU/2018/089}).
 Additionally, it has been backed by the work of both COST Actions: \texttt{CA19134} -- \textit{``Distributed Knowledge Graphs''} and \texttt{CA19142} -- \textit{``Leading Platform for European Citizens, Industries, Academia and Policymakers in Media Accessibility''}.

### 2021-06-29 paper/paper.tex
Add labels

@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.6\textwidth]{labels.png}
+  \caption{Graphical representation of the relative difficulty of each type of annotation.
+We compute the relative number of systems that correctly identified each annotation of each type.
+Boxplots show the mininum, maximum, and interquartile range.\label{fig:labels}}
+\end{figure*}
+
+Figure~\ref{fig:labels} compares annotation labels according to their relative difficulty.
+We define the difficulty of a specific annotation~(e.g., a specific entity or relation instance in the testing set) as the relative number of systems that correctly identified that annotation.
+Afterwards, we compute the interquartile range of the difficulty score for each of the annotations in the testing set.
+The figure suggests that entities are, on average, easier to recognize than relations, which is consistent with the superior results obtained in Subtask A compared to Subtask B by all participants.
+
 Modelling both subtasks independently seems to be less effective than using some form of shared architecture.
@@
 
-\todo[inline]{Grafica de dispersion dificultad para identificar cada tipo de etiqueta}
-
 \section{Conclusions}\label{sec:conclusions}
